### 2021-06-01 paper/paper.tex
made the code more readable and started righting a simple tex file about the implementation and the results

\documentclass[11pt]{article}
    \title{\textbf{Causal graph quantum dynamic simulation}}
    \author{auteurs...}
    \date{}

    \setlength{\parindent}{0cm}

    \addtolength{\topmargin}{-3cm}
    \addtolength{\textheight}{3cm}
    \usepackage[margin=0.5in]{geometry}

    \usepackage{xcolor}
	\usepackage{listings}

	\definecolor{mGreen}{rgb}{0,0.6,0}
	\definecolor{mGray}{rgb}{0.5,0.5,0.5}
	\definecolor{mPurple}{rgb}{0.58,0,0.82}
	\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}

	\lstdefinestyle{CStyle}{
		backgroundcolor=\color{backgroundColour},   
		commentstyle=\color{mGreen},
		keywordstyle=\color{magenta},
		numberstyle=\tiny\color{mGray},
		stringstyle=\color{mPurple},
		basicstyle=\footnotesize,
		breakatwhitespace=false,         
		breaklines=true,                 
		captionpos=b,                    
		keepspaces=true,                 
		numbers=left,                    
		numbersep=5pt,                  
		showspaces=false,                
		showstringspaces=false,
		showtabs=false,                  
		tabsize=2,
		language=C
	}
\begin{document}

\maketitle
\thispagestyle{empty}

\section{Introduction}

\section{Results}

\section{Tests}

We did some tests to validate the simulations, including (but not limitted to) the classical and quantum injectivity tests.

\subsection{classical injectivity test}

To check if our graph dynamics is reversible, we can apply on a huge number of random graphs a single step, and a reversed step and check that we get back the same graph with started with.\\

This was tested on arround 10k graphs, for chich the particules position were radomized, but the graph name was kept, making it more complex as each step on random particules positions caused splits and merges.

\subsection{quantum injectivity test}

To check that our graph dynamic is unitary, we can check that computing an arbitrary amount of steps on an arbitrary initial state (incrissing drasticly the number of graphs), and then apply the same number of reversed step, and we check that we get back the state we started with.\\

Even including floating points errors, we can esaily do this test with around 5 steps, obtain around 200k graphs after the 5 forward iteration, and comme back to the same step within 0.001\% error in the magnitude.

\section{Implementation}

The code shown below is a simplification of the actual code  \footnote{https://github.com/jolatechno/Quantum-graph-simulation.git} (classes are shown without member function or decorators, and code inside loops is represented by functions).\\

The folllowing classes are used in the implementation:

\begin{description}
\addtolength{\itemindent}{0.80cm}
\itemsep0em 
\item[node names] corresponding to the name \footnote{arithmetique de nom} of a single node.
\item[graph names] i.e. ordered set of node.
\item[graphs with particules] graph name and positions of particules.
\item[superposition of graphs]
\end{description}

\subsection{node names}

Nodes can either be "left" or "right" containers (pointing to another node), "elemnts" (a simple integer name) or pairs (a merge of two other nodes, pointing to two other nodes).\\

We mark each node with a "has\_most\_left\_zero\_" (which is inerited through merges)  variable to keep track of the node that contains the first nodes.

\subsubsection{class}

\begin{lstlisting}[style=CStyle]
struct node {
	int left_idx__or_element_;
	int right_idx__or_type_;
	size_t hash_ = 0;
	bool has_most_left_zero_ = false;
	//...
\end{lstlisting}

\subsubsection{constructors}

The following constructor helps construct an "element-type" node (which are just a single integer, and are used to initialize graphs):

\begin{lstlisting}[style=CStyle]
	//...
	node(int n) :
		left_idx__or_element_(n), right_idx__or_type_(element_idx) {

		hash_ = n;
		boost::hash_combine(hash_, element_idx);

		has_most_left_zero_ = n == 0;
	}
	//...
\end{lstlisting}

We also need a constructor for "left/eright-type" node (noted "u.l" or "u.r"):

\begin{lstlisting}[style=CStyle]
	//...
	node(int const idx, node_t const &other, int const type) :
		left_idx__or_element_(idx), right_idx__or_type_(type) {

		boost::hash_combine(hash_, other.hash_);
		boost::hash_combine(hash_, type);

		// check for most left zero
		if (is_left())
			has_most_left_zero_ = other.has_most_left_zero_;
	}
	//...
\end{lstlisting}

And finally, we need a constructor to construct "pair-type" nodes (noted "u$\wedge$v"):

\begin{lstlisting}[style=CStyle]
	//...
	node(int const left_idx, node_t const &left,
		int const right_idx, node_t const &right) :
		left_idx__or_element_(left_idx),
		right_idx__or_type_(right_idx){

		boost::hash_combine(hash_, left.hash_);
		boost::hash_combine(hash_, right.hash_);
		has_most_left_zero_ = left.has_most_left_zero_ || right.has_most_left_zero_;
	}
	//...
}
\end{lstlisting}

\subsubsection{hash}

the hash of a node is stored in the "hash\_" varibale, and is simply calculated by the constructor (since it never changes).\\

To compute the hash of a node, we simply combine the hash of all children nodes or of the integer representing the element, and/or the type of the node.

\subsection{graph names}

To store the list of nodes, we use a main nodes list, which we keep in a lexicographical order (the first node should always be the node with the "most left zero").\\

Other nodes which are pointed to are stored into a buffer vector, for which we use grabage collection.

\subsubsection{class}

\begin{lstlisting}[style=CStyle]
class graph_name {
private:
	// node list 
	std::vector<node_t> nodes_;
	std::vector<node_t> node_buff_;
	std::vector<int> trash_collection_;

	// hash
	size_t mutable hash_ = 0;
	bool mutable hashed_ = false;

	//...
\end{lstlisting}

\subsubsection{usefull functions}

Since we use trash collection to manage memory, we need to implement a collection to insert a node into the "buffer vector":

\begin{lstlisting}[style=CStyle]
	//...
	int push_to_buffer(node_t &n) {
		if (trash_collection_.empty()) {
			node_buff_.push_back(n);
			return node_buff_.size() - 1;
		}

		int buff_idx = trash_collection_.back();
		trash_collection_.pop_back();
		node_buff_[buff_idx] = n;
		return buff_idx;
	}
	//...
\end{lstlisting}

\subsubsection{split}

\begin{lstlisting}[style=CStyle]
	//...
	bool inline split(unsigned int idx) {
		hashed_ = false;

		node_t node = nodes_[idx];
		if (node.is_pair()) {
			// read indexes
			int const left_idx = node.left_idx();
			int const right_idx = node.right_idx();

			// add left node
			nodes_[idx] = node_buff_[left_idx];
			trash_collection_.push_back(left_idx);

			// add right node
			nodes_.insert(nodes_.begin() + idx + 1, node_buff_[right_idx]);
			trash_collection_.push_back(right_idx);

			// check if we should rotate
			if (idx == 0 && nodes_[1].has_most_left_zero()) {
				std::rotate(nodes_.begin(), nodes_.begin() + 1, nodes_.end());
				return true; 
			}

			return false;
		}

		// add current node to buffer
		int buff_idx = push_to_buffer(node);

		// add left node
		nodes_[idx] = node_t(buff_idx, node, point_l_idx);

		// add right node
		nodes_.insert(nodes_.begin() + idx + 1,
			node_t(buff_idx, node, point_r_idx));

		return false;
	}
	//...
\end{lstlisting}

The boolean return argument of this function is used to check if the merge requires a rotation of nodes.

\subsubsection{merges}

\begin{lstlisting}[style=CStyle]
	//...
	void inline merge(unsigned int idx) {
		hashed_ = false;

		// destination idx
		unsigned int right_idx = (idx + 1) % size();
		auto left = nodes_[idx];
		auto right = nodes_[right_idx];

		if (left.is_left() && right.is_right()) {
			int const left_left = left.left_idx();
			int const right_left = right.left_idx();

			if (node_buff_[left_left].hash() == node_buff_[right_left].hash()) {
				// trash collect
				trash_collection_.push_back(left_left);
				if (left_left != right_left)
					trash_collection_.push_back(right_left);

				//add node
				nodes_[right_idx] = node_buff_[left_left];
				nodes_.erase(nodes_.begin() + idx);
				return;
			}
		}

		//add node
		int const left_idx = push_to_buffer(left);
		int const right_idx_ = push_to_buffer(right);

		nodes_[right_idx] = node_t(left_idx, left, right_idx_, right);
		nodes_.erase(nodes_.begin() + idx);
	}
	//...
\end{lstlisting}

\subsubsection{hash()}

To hash a graph name, we simply combine the hash of all the nodes.

\begin{lstlisting}[style=CStyle]
	//...
	size_t inline hash() const {
		if (hashed_)
			return hash_;

		hash_ = 0;

		/* combine all nodes hash */
		for (auto &n : nodes_)
			boost::hash_combine(hash_, n.hash());

		hashed_ = true;
		return hash_;
	}
	//...
}
\end{lstlisting}

\subsection{graphs with particules}

A graph is represented by a graph name, and an ordered list of the node's index of particules going both ways.

\subsubsection{class}

\begin{lstlisting}[style=CStyle]
class graph {
	// variables 
	graph_name_t* name_;
	std::vector<unsigned int> left_;
	std::vector<unsigned int> right_;

	// hash
	size_t mutable hash_ = 0;
	bool mutable hashed_ = false;

	//...
\end{lstlisting}

\subsubsection{step and reversed\_step()}

The fonction to step all particules uses the fonctions "rotate\_once\_left" and "rotate\_once\_right" which rotate particules if they overflow:

\begin{lstlisting}[style=CStyle]
	//...
	void inline step() {
  		hashed_ = false;

  		rotate_once_right(right_);
  		rotate_once_left(left_);
  	}
  	//...
\end{lstlisting}

To implement the reverse stpe we simply exchange the roles of "left" and "right" in the "step" function:

\begin{lstlisting}[style=CStyle]
	//...
  	void inline reversed_step() {
  		hashed_ = false;

  		rotate_once_right(left_);
  		rotate_once_left(right_);
  	}
  	//...
\end{lstlisting}

\subsubsection{split\_merge()}

\begin{lstlisting}[style=CStyle]
	//...
	void split_merge(std::vector<split_merge_t>& split_merge) {
		/* first check if there are any split or merges */

		hashed_ = false;

		// check for last merge 
		/* ... */
		if (last_merge()) {
			name_->merge(last_idx);
			overflow_right(left_);
			split_merge.pop_back();
			/* ... */
		}

		// check for first element split 
		bool first_split = false;

		// split and merge names 
		// and calculating max displacement 
		int total_displacement = 0;
		for (auto split_merge_it = split_merge.rbegin(); split_merge_it != split_merge.rend(); ++split_merge_it)
			if ((*split_merge_it).second == split_t) {
				first_split |= name_->split((*split_merge_it).first) && (*split_merge_it).first == 0;

				++total_displacement;
			} else {
				name_->merge((*split_merge_it).first);
				--total_displacement;
			}

		// move particules 
		int displacement = total_displacement;
		auto split_merge_it = last_split_merge;
		for (auto left_it = left_.rbegin(); left_it != left_.rend(); ++left_it) {
			// check if there are any nodes left 
			while (split_merge_it >= split_merge.begin()) {
				// check if the node is split or merged 
				if ((*split_merge_it).first >= *left_it) {
					if ((*split_merge_it).second == split_t) {
						--displacement; // decrement the displacement 
					} else
						++displacement; // decrement the displacement 
					--split_merge_it;
				} else
					break;

			}

			if (split_merge_it == split_merge.begin() && displacement == 0)
				break;

			*left_it += displacement;
		}

		/* we than do the exact same thing with particule going to the right, rplacing ">=" at line 48 by a ">" */

		// finish first split 
		if (first_split) {
			rotate_once_left(left_);
			rotate_once_left(right_);
		}
	}
	//...
\end{lstlisting}

\subsubsection{hash()}

To hash graphs we simply combine all the positions of partricules going in one directions, a separator, the paricules going the other, a separator way and finally the hash of the graph's name.

\begin{lstlisting}[style=CStyle]
	//...
	size_t hash() const {
		if (hashed_)
			return hash_;

		hash_ = 0;
		boost::hash<unsigned int> hasher;

		// left hash 
		for (auto &l : left_)
			boost::hash_combine(hash_, l);

	 	 // separator 
	  	boost::hash_combine(hash_, separator);

	  	// right hash 
	  	for (auto &r : right_)
	   		boost::hash_combine(hash_, r);

	  	// separator 
	  	boost::hash_combine(hash_, separator);

	  	// name hash 
	  	boost::hash_combine(hash_, name_->hash());

	  hashed_ = true;
	  return hash_;
	}
	//...
}
\end{lstlisting}

\subsubsection{get\_split\_merges()}

To get the list of all indeces of splits and merges, we iterate through both the "left" and "right" positions, iterating the one that is the smallest so that it always converges towars positions that match (or are one apart for merges):

\begin{lstlisting}[style=CStyle]
/* function to get all split and merges */
std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
	std::vector<graph::split_merge_t> split_merge;

	/* first check if there are any particules to check */

	/* definition of left_it, right_it, last_left, last_right ... */

	bool first_or_last_split = *left_it == *right_it && *left_it == 0;
	while (true) {
		/* check if there are any particules left after iterating */
		if (right_it > last_right ||
		left_it > last_left)
			break;

		if (*left_it == *right_it) {
			/* check for split */
			split_merge.push_back({(*left_it), graph->split_t});

			/* check for last split */
			if (*right_it == last_idx)
				first_or_last_split = true;

			++right_it;
			++left_it;
		} else if (*left_it < *right_it) {
			/* chedk for merges */
			if (*left_it == *right_it - 1)
				if (left_it == last_left) {
					split_merge.push_back({(*left_it), graph->merge_t});
				} else if (*(left_it + 1) != *right_it)
					split_merge.push_back({(*left_it), graph->merge_t});

			++left_it;
		} else
			++right_it;
	}

	if (!first_or_last_split)
		if (*last_left == last_idx &&
		graph->right()[0] == 0)
			split_merge.push_back({last_idx, graph->merge_t});

	return split_merge;
}
\end{lstlisting}

\subsection{superposition of graphs}

\subsubsection{class}

To allow parallel insertions of graphs into the lists of all graphs, we use tbb concurent hashmap. \\

We make the approximation that graphs with the same hash are equals and should therefor interact.

\begin{lstlisting}[style=CStyle]
class state {
	// hasher
	struct graph_hasher { /* */ }

	// comparator
	struct graph_comparator { /* */ }

	// type definition
	typedef tbb::concurrent_unordered_multimap<graph_t*, std::complex<long double>, graph_hasher, graph_comparator> graph_map_t;

	// main list 
	graph_map_t graphs_;

	// parameters
	std::complex<long double> non_merge_ = -1;
	std::complex<long double> merge_ = 0;

	//..
\end{lstlisting}

\subsubsection{subset of splist and merges}

We first need to know the number of possible graphs from the lists of splits and merges:

\begin{lstlisting}[style=CStyle]
template<class T>
int num_subset(std::vector<T> const &vect) {
	return pow(2, vect.size());
}
\end{lstlisting}

We can then associate a number between 0 and "num\_subset" to a certain compositions of all the splits and merges (by seeing the nth binary ditgit of this number as enabling the nth split or merge) :

\begin{lstlisting}[style=CStyle]
std::pair<std::vector<graph::split_merge_t>, std::complex<long double>> subset(std::vector<graph::split_merge_t>& split_merge, int subset_numb,
	std::complex<long double>& non_merge, std::complex<long double>& merge) {

	std::vector<graph::split_merge_t> res;
	std::complex<long double> proba = 1;

	for (int i = 0; i < split_merge.size(); ++i) {
		long double sign = 1 - 2*split_merge[i].second;

		/* i_th bit of subset_numb */
		if (subset_numb%2) {
			/* add opperation to res */
			res.push_back(split_merge[i]);

			/* get proba */
			proba *= std::complex<long double>(merge.real(), sign*merge.imag());
		} else
			proba *= sign*non_merge;

		subset_numb /= 2;
	}

	return {res, proba};
}
\end{lstlisting}

\subsubsection{reduce\_all()}

\begin{lstlisting}[style=CStyle]
\end{lstlisting}

\subsubsection{step\_split\_merge\_all() and reversed\_split\_merge\_step\_all()}

\begin{lstlisting}[style=CStyle]
\end{lstlisting}

\subsubsection{source of errors}

\end{document}

### 2021-06-01 v4/classical/graph.hpp

@@ -11,7 +11,7 @@
 
 // forward declaration of the graph_t type 
 typedef class graph graph_t;
-size_t const separator = boost::hash<int>{}(-1); 
+size_t const separator = -1; 
 
 class graph {
 private:
@@ -114,20 +114,21 @@ size_t graph::hash() const {
 
 	// left hash 
 	for (auto &l : left_)
-		boost::hash_combine(hash_, hasher(l));
+		boost::hash_combine(hash_, l);
 
-  // separator 
-  boost::hash_combine(hash_, separator);
+ 	 // separator 
+  	boost::hash_combine(hash_, separator);
 
-  // right hash 
-  for (auto &r : right_)
-   	boost::hash_combine(hash_, hasher(r));
+  	// right hash 
+  	for (auto &r : right_)
+   		boost::hash_combine(hash_, r);
 
-  // separator 
-  boost::hash_combine(hash_, separator);
+  	// separator 
+  	boost::hash_combine(hash_, separator);
 
-  // name hash 
-  boost::hash_combine(hash_, name_->hash());
+  	// name hash 
+  	boost::hash_combine(hash_, name_->hash());
+		
 
   hashed_ = true;
   return hash_;
@@ -176,12 +177,12 @@ void graph::rotate_once_right(std::vector<unsigned int>& pos) {
 
 // split merge 
 void graph::split_merge(std::vector<split_merge_t>& split_merge) {
-	hashed_ = false;
-
 	if (left_.size() == 0 ||
 	right_.size() == 0 ||
 	split_merge.size() == 0)
 		return;
+	
+	hashed_ = false;
 
 	// check for last merge 
 	auto last_split_merge = split_merge.end() - 1;

### 2021-06-01 v4/classical/graph_name.hpp

@@ -15,6 +15,10 @@ private:
 	std::vector<node_t> node_buff_;
 	std::vector<int> trash_collection_;
 
+	// hash
+	size_t mutable hash_ = 0;
+	bool mutable hashed_ = false;
+
 	int push_to_buffer(node_t &n) {
 		if (trash_collection_.empty()) {
 			node_buff_.push_back(n);
@@ -58,14 +62,18 @@ public:
 	}
 
 	//hasher
-	size_t hash() {
-		size_t h = 0;
+	size_t inline hash() const {
+		if (hashed_)
+			return hash_;
+
+		hash_ = 0;
 
 		/* combine all nodes hash */
 		for (auto &n : nodes_)
-			boost::hash_combine(h, n.hash());
+			boost::hash_combine(hash_, n.hash());
 
-		return h;
+		hashed_ = true;
+		return hash_;
 	}
 
 	// split and merge 
@@ -75,8 +83,9 @@ public:
 
 // split merge
 bool inline graph_name::split(unsigned int idx) {
-	node_t node = nodes_[idx];
+	hashed_ = false;
 
+	node_t node = nodes_[idx];
 	if (node.is_pair()) {
 		// read indexes
 		int const left_idx = node.left_idx();
@@ -103,16 +112,18 @@ bool inline graph_name::split(unsigned int idx) {
 	int buff_idx = push_to_buffer(node);
 
 	// add left node
-	nodes_[idx] = node_t(buff_idx, point_l_idx, node_buff_);
+	nodes_[idx] = node_t(buff_idx, node, point_l_idx);
 
 	// add right node
 	nodes_.insert(nodes_.begin() + idx + 1,
-		node_t(buff_idx, point_r_idx, node_buff_));
+		node_t(buff_idx, node, point_r_idx));
 	
 	return false;
 }
 
 void inline graph_name::merge(unsigned int idx) {
+	hashed_ = false;
+
 	// destination idx
 	unsigned int right_idx = (idx + 1) % size();
 	auto left = nodes_[idx];
@@ -139,7 +150,7 @@ void inline graph_name::merge(unsigned int idx) {
 	int const left_idx = push_to_buffer(left);
 	int const right_idx_ = push_to_buffer(right);
 
-	nodes_[right_idx] = node_t(left_idx, right_idx_, node_buff_);
+	nodes_[right_idx] = node_t(left_idx, left, right_idx_, right);
 	nodes_.erase(nodes_.begin() + idx);
 }
 

### 2021-06-01 v4/classical/node.hpp

@@ -21,25 +21,32 @@ private:
 public:
 
 	// constructors
-	node(int n) : left_idx__or_element_(n), right_idx__or_type_(element_idx) {
-		hash_ = boost::hash<int>{}(n);
+	node(int n) :
+		left_idx__or_element_(n), right_idx__or_type_(element_idx) {
+
+		hash_ = n;
+		boost::hash_combine(hash_, element_idx);
+		
 		has_most_left_zero_ = n == 0;
 	}
 
-	node(int const left_idx, int const right_idx__or_type, std::vector<node_t> const &node_buff) : left_idx__or_element_(left_idx), right_idx__or_type_(right_idx__or_type) {
-		boost::hash_combine(hash_, node_buff[left_idx].hash_);
+	node(int const idx, node_t const &other, int const type) :
+		left_idx__or_element_(idx), right_idx__or_type_(type) {
 
-		// check if right_idx__or_type is an index or a type
-		if (right_idx__or_type >= 0) {
-			boost::hash_combine(hash_, node_buff[right_idx__or_type].hash_);
-			has_most_left_zero_ = node_buff[left_idx].has_most_left_zero_ || node_buff[right_idx__or_type].has_most_left_zero_;
-		} else {
-			boost::hash_combine(hash_, right_idx__or_type);
+		boost::hash_combine(hash_, other.hash_);
+		boost::hash_combine(hash_, type);
 
-			// check for most left zero
-			if (is_left())
-				has_most_left_zero_ = node_buff[left_idx].has_most_left_zero_;
-		}
+		// check for most left zero
+		if (is_left())
+			has_most_left_zero_ = other.has_most_left_zero_;
+	}
+
+	node(int const left_idx, node_t const &left, int const right_idx, node_t const &right) :
+		left_idx__or_element_(left_idx), right_idx__or_type_(right_idx){
+
+		boost::hash_combine(hash_, left.hash_);
+		boost::hash_combine(hash_, right.hash_);
+		has_most_left_zero_ = left.has_most_left_zero_ || right.has_most_left_zero_;
 	}
 
 	// getters

### 2021-06-01 v4/classical/rules.hpp

@@ -28,7 +28,7 @@ std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
 
 		if (*left_it == *right_it) {
 			/* check for split */
-			split_merge.push_back(std::pair<unsigned int, graph::split_merge_type_t>((*left_it), graph->split_t));
+			split_merge.push_back({(*left_it), graph->split_t});
 
 			/* check for last split */
 			if (*right_it == last_idx)
@@ -40,9 +40,9 @@ std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
 			/* chedk for merges */
 			if (*left_it == *right_it - 1)
 				if (left_it == last_left) {
-					split_merge.push_back(std::pair<unsigned int, graph::split_merge_type_t>((*left_it), graph->merge_t));
+					split_merge.push_back({(*left_it), graph->merge_t});
 				} else if (*(left_it + 1) != *right_it)
-					split_merge.push_back(std::pair<unsigned int, graph::split_merge_type_t>((*left_it), graph->merge_t));
+					split_merge.push_back({(*left_it), graph->merge_t});
 
 			++left_it;
 		} else
@@ -52,7 +52,7 @@ std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
 	if (!first_or_last_split)
 		if (*last_left == last_idx &&
 		graph->right()[0] == 0)
-			split_merge.push_back(std::pair<unsigned int, graph::split_merge_type_t>(last_idx, graph->merge_t));
+			split_merge.push_back({last_idx, graph->merge_t});
 
 	return split_merge;
 }

### 2021-06-01 v4/tests/classical_injectivity_test.cpp

@@ -1,0 +1,38 @@
+#include "../classical/rules.hpp"
+#include "../classical/graph.hpp"
+#include "../classical/checks.hpp"
+#include <stdio.h>
+
+int main() {
+  for (int j = 0; j < 1000; ++j) {
+    
+    graph_t* g = new graph(10);
+
+    for (int i = 0; i < 20; ++i) {
+      g->randomize();
+      graph_t* c = g->copy();
+
+      g->step();
+      auto split_merge = get_split_merge(g);
+      g->split_merge(split_merge);
+
+      graph_t* c2 = g->copy();
+
+      split_merge = get_split_merge(c2);
+      c2->split_merge(split_merge);
+      c2->reversed_step();
+
+
+      if (c2->hash() != c->hash() /*!g->equal(c)*/){
+        c2->print(); printf("\n");
+        c->print(); printf("\n");
+        return -2;
+      }
+
+      if (!graph_checker(g))
+        return -1;
+    }
+  }
+    
+  printf("Ok\n");
+}

### 2021-06-01 v4/tests/injectivity_test.cpp

@@ -1,29 +1,0 @@
-#include "../classical/rules.hpp"
-#include "../classical/graph.hpp"
-#include "../classical/checks.hpp"
-#include <stdio.h>
-
-int main() {
-  graph_t* g = new graph(20);
-
-  for (int i = 0; i < 100000; ++i) {
-    g->randomize();
-    graph_t* c = g->copy();
-
-    auto split_merge = get_split_merge(g);
-    g->split_merge(split_merge);
-
-    split_merge = get_split_merge(g);
-    g->split_merge(split_merge);
-
-    if (g->hash() != c->hash() /*!g->equal(c)*/){
-      c->print(); printf("\n");
-      g->print(); printf("\n");
-      return -2;
-    }
-
-    if (!graph_checker(g))
-      return -1;
-  }
-  printf("Ok\n");
-}

### 2021-06-01 v4/tests/quantum_injectivity_test.cpp

@@ -68,7 +68,7 @@ loop:
 		state_t* s = new state(g_1);
 		s->set_params(M_PI_4, M_PI_4);
 
-		int n_iter = 4;
+		int n_iter = 5;
 
 		for (int i = 0; i < n_iter; ++i) {
 			s->step_split_merge_all();

### 2021-06-02 paper/paper.tex
optimized the reduce step

@@
 \begin{lstlisting}[style=CStyle]
+	//...
+	void reduce_all() {
+		for(auto it = graphs_.begin(); it != graphs_.end();) {
+    	// range of similar graphs to delete
+    	auto range = graphs_.equal_range(it->first);
+    	auto start = range.first;
+
+    	for(auto jt = std::next(it); jt != range.second; ++jt)
+        	it->second += jt->second;
+
+    	// if the first graphgs has a zero probability, erase the whole range
+    	if (!check_zero(it->second))
+    		++start;
+
+    	it = graphs_.unsafe_erase(start, range.second);
+	}
+	//...
 \end{lstlisting}
@@
 \begin{lstlisting}[style=CStyle]
+	//...
+	void step_split_merge_all(bool step, bool split_merge, bool reversed) {
+		graph_map_t buff;
+		buff.swap(graphs_);
+
+		#pragma omp parallel
+		#pragma omp single
+	  	for (auto & [graph, mag] : buff)
+		#pragma omp task
+	  	{
+	  		if (step)
+	  			graph->step();
+
+	  		if (reversed)
+	  			graph->reversed_step();
+
+	  		if (split_merge) {
+	  			auto split_merge = get_split_merge(graph);
+
+				// add all graphs that actually have some split ot merge 
+				const int n_max = num_subset(split_merge);
+				#pragma omp taskloop
+				for (int j = 1; j < n_max; ++j) {
+					graph_t* g_ = graph->copy();
+
+					auto [split_merge_list, mag_split_merge] = subset(split_merge, j, non_merge_, merge_);
+				  	g_->split_merge(split_merge_list);
+
+				  	//add graph
+				  	graphs_.insert({g_, mag * mag_split_merge});
+				}
+				// update the probability of the graph without split or merge 
+				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
+				mag *= mag_no_split_merge;
+	  		}
+
+	  		//add graph
+			graphs_.insert({graph, mag});
+	  	}
+	}
+	//...
 \end{lstlisting}

### 2021-06-02 v4/quantum/state.hpp

@@ -84,41 +84,15 @@ void state::reduce_all() {
 		printf("reducing %ld graphs...\n", graphs_.size());
 	#endif
 
-	// Select the correct type for calling the equal_range function
-    decltype(graphs_.equal_range(0)) range;
-
-    // iterate through multimap's elements (by key)
-	#pragma omp parallel
-	#pragma omp single
-    for(auto it = graphs_.begin(); it != graphs_.end(); it = range.second) {
-        // Get the range of the current key
-        range = graphs_.equal_range(it->first);
-
-        // save the range
-        auto const jt = range.first;
-        const auto local_end = range.second;
-        
-        // next iterator
-        auto kt = jt;
-        ++kt;
-
-        // Now sum out that whole range
-		#pragma omp task
-        for(; kt != local_end; ++kt)
-        	jt->second += kt->second;
-    }
-
-    #ifdef VERBOSE
-		printf("erasing graphs...\n");
-	#endif
-
-    /* erase zero probability graphs */
     for(auto it = graphs_.begin(); it != graphs_.end();) {
-    	/* range of similar graphs to delete */
-    	range = graphs_.equal_range(it->first);
+    	// range of similar graphs to delete
+    	auto range = graphs_.equal_range(it->first);
     	auto start = range.first;
 
-    	/* if the first graphgs has a zero probability, erase the whole range */
+    	for(auto jt = std::next(it); jt != range.second; ++jt)
+        	it->second += jt->second;
+
+    	// if the first graphgs has a zero probability, erase the whole range
     	if (!check_zero(it->second))
     		++start;
 

### 2021-06-02 paper/paper.tex
deleted older version and continued optimizing

@@
 	//...
-	void step_split_merge_all(bool step, bool split_merge, bool reversed) {
+	void step_split_merge_all() {
 		graph_map_t buff;
@@
 	  	{
-	  		if (step)
-	  			graph->step();
 
-	  		if (reversed)
-	  			graph->reversed_step();
+	  		graph->step(); //graph->reversed_step(); for reversed_split_merge_step_all()
 
-	  		if (split_merge) {
 	  		auto split_merge = get_split_merge(graph);
+
+	  		#pragma omp task
+	  		{
+	  			// update the probability of the graph without split or merge 
+				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
+				graphs_.insert({graph, mag * mag_no_split_merge});
+	  		}
 
@@
 	  		}
-				// update the probability of the graph without split or merge 
-				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
-				mag *= mag_no_split_merge;
-	  		}
-
-	  		//add graph
-			graphs_.insert({graph, mag});
 	  	}

### 2021-06-02 v1/class.hpp

@@ -1,93 +1,0 @@
-#include <omp.h> //for parralelism
-#include <stdbool.h> //for bool
-#include <cstdlib> //for malloc etc..
-#include <vector> //for vector
-
-/*
-defining flags
-*/
-
-
-#define STRATEGY_INTERACT_ALL 0
-#define STRATEGY_INTERACT_NONE 1
-void print_list(int *list, int size);
-
-
-/*
-state class definition
-*/
-
-
-typedef class state {
-private:
-  int sort_in_place();
-  #pragma omp declare target
-  int inline overflowed_clockwise();
-  int inline overflowed_conter_clockwise();
-  #pragma omp end declare target
-public:
-  bool color = false;
-  double probability = 1;
-  size_t n_nodes;
-  size_t n_particules, n_clockwise = 0;
-  int *particules;
-
-  state(size_t n) { //allocate
-    n_particules = n;
-    particules = (int*)malloc(n*sizeof(int));
-  }
-  ~state() { //free
-    free(particules);
-  }
-
-  int randomize();
-  int randomize(int n_clockwise_);
-  state* copy();
-  #pragma omp declare target
-  bool inline equal(state *other);
-  int inline switch_direction(int i);
-  int inline split_node(int node);
-  int inline split_nodes(int *nodes, int size);
-  int inline merge_node(int node);
-  int inline merge_nodes(int *nodes, int size);
-  int inline merge_split(int* split_list, int split_size, int* merge_list, int merge_size);
-  int inline step_all();
-  #pragma omp end declare target
-} state;
-
-
-/*
-class defining the rule of an interaction
-*/
-
-
-typedef class rule {
-public:
-  #pragma omp declare target
-  int inline get_merge(state *s, int* list_merge, int *n_merge);
-  int inline get_split(state *s, int* list_split, int *n_split);
-  #pragma omp end declare target
-} rule;
-
-
-/*
-------------------------------------------------------------
-FOR QUANTUM CASE ONLY:
-------------------------------------------------------------
-state_list class definition
-*/
-
-
-typedef class state_list {
-public:
-  double prob_min;
-  std::vector<state*> states;
-
-  state_list(); //TODO
-
-  int step_all(rule* r);
-  #pragma omp declare target
-  int add_state(state *s);
-  int step(double interaction_prob);
-  #pragma omp end declare target
-} state_list;

### 2021-06-02 v1/main.cpp

@@ -1,51 +1,0 @@
-/*
-compile using:
-
-g++ main.cpp -fopenmp -foffload=nvptx-none -fcf-protection=none -fno-stack-protector
-*/
-
-#include <time.h> //for the random seed
-
-#include "class.hpp"
-
-#include "debuging.inl"
-#include "rule.inl"
-#include "state.inl"
-#include "quantum_state.inl"
-
-#define N_RUNS 5
-#define N_ITER 5000
-#define N_PARTICULES 100
-#define N_NODE0 500
-
-
-int main() {
-  srand (time(NULL)); //initialize random seed
-  rule *ref = new rule();
-
-  int split_size, *split_indexes = (int*)malloc(N_PARTICULES*sizeof(int));
-  int merge_size, *merge_indexes = (int*)malloc(N_PARTICULES*sizeof(int));
-
-  for (int j = 0; j < N_RUNS; j++) {
-    state *s = new state(N_PARTICULES);
-    s->n_nodes = N_NODE0;
-    s->randomize(N_PARTICULES/2);
-
-    for (int i = 0; i < N_ITER; i++) {
-      s->step_all();
-      ref->get_split(s, split_indexes, &split_size);
-      ref->get_merge(s, merge_indexes, &merge_size);
-      s->merge_split(split_indexes, split_size, merge_indexes, merge_size);
-
-      printf("%ld", s->n_nodes);
-      if (i != N_ITER - 1)
-        printf(",");
-    }
-    if (j != N_RUNS - 1)
-      printf(";");
-  }
-
-  printf("\n");
-
-  return 0;
-}

### 2021-06-02 v1/tests/test_reversibility.cpp

@@ -1,100 +1,0 @@
-/*
-compile using:
-
-g++ test_reversibility.cpp -fopenmp -foffload=nvptx-none -fcf-protection=none -fno-stack-protector
-*/
-
-#include "../class.hpp"
-
-#include "../debuging.inl"
-#include "../rule.inl"
-#include "../state.inl"
-#include "../quantum_state.inl"
-
-#include "reversibility_test.inl"
-
-#define SIZE 4
-#define PRINT 64
-
-int main() {
-  rule *ref = new rule();
-
-  int num_graphs = number_of_graphs(SIZE);
-  state** state_list = list_all_graphs(SIZE);
-
-  for (long int i = 0; i < PRINT; i++) {
-    printf("%ld: ", i); print_state(state_list[i]);
-  }
-
-  printf("is distinct: %s\n", check_distinct(state_list, num_graphs) ? "true" : "false");
-
-  state **new_state_list = (state**)malloc(num_graphs*sizeof(state*));
-
-  //#pragma omp parallel for
-  for (int i = 0; i < num_graphs; i++) {
-    state *s = state_list[i]->copy(); //state to consider
-    const int n_particules = s->n_particules; //numer of particules
-
-    // list for interactions
-    int split_size, *split_indexes = (int*)malloc(n_particules*sizeof(int));
-    int merge_size, *merge_indexes = (int*)malloc(n_particules*sizeof(int));
-
-    //apply an iteration
-    s->step_all();
-    ref->get_split(s, split_indexes, &split_size);
-    ref->get_merge(s, merge_indexes, &merge_size);
-    s->merge_split(split_indexes, split_size, merge_indexes, merge_size);
-
-    if (!check(s)) {
-      print_state(s);
-      printf("with %ld particules\n\n", s->n_particules);
-    }
-
-    new_state_list[i] = s;
-  }
-
-  for (long int i = 0; i < PRINT; i++) {
-    printf("%ld: ", i); print_state(new_state_list[i]);
-  }
-
-  /*
-  debugging information
-  */
-
-
-  int i, j;
-  bool distinct = check_distinct(new_state_list, num_graphs, &i, &j);
-  printf("is distinct: %s\n", distinct ? "true" : "false");
-
-  if (!distinct) {
-    print_state(state_list[i]);
-    print_state(state_list[j]);
-
-    printf("with %ld particules \n\n", state_list[i]->n_particules);
-
-    state_list[i]->step_all();
-    state_list[j]->step_all();
[…]

### 2021-06-02 v2/graph.hpp

@@ -1,44 +1,0 @@
-#pragma once
-#include "node.hpp"
-#include "graph_names.hpp"
-
-typedef class graph {
-private:
-  /* graph name */
-  graph_name* name;
-
-  /* round shift */
-  void circular_shift_left(std::vector<int> &list);
-  void circular_shift_right(std::vector<int> &list);
-
-  /* split and merge on list */
-  void _split_left(std::vector<int> &positions, std::vector<int> &nodes);
-  void _split_right(std::vector<int> &positions, std::vector<int> &nodes);
-  void _merge(std::vector<int> &positions, std::vector<int> &nodes, int n_nodes);
-public:
-  /* number of nodes */
-  int num_nodes();
-
-  /* particules list */
-  std::vector<int> left;
-  std::vector<int> right;
-
-  /* constructor */
-  graph(int size);
-  graph* copy();
-  void randomize(int n_left, int n_right);
-
-  /* comparison tools */
-  bool equal(graph* other);
-
-  /* split and merge */
-  void split(std::vector<int> &nodes);
-  void merge(std::vector<int> &nodes);
-  void split_merge(std::vector<int> &split_nodes, std::vector<int> &merge_nodes);
-  void step_all();
-
-  /* debuging */
-  void print();
-  void print_name();
-
-} graph;

### 2021-06-02 v2/graph_names.hpp

@@ -1,29 +1,0 @@
-#pragma once
-#include "node.hpp"
-
-typedef class graph_name {
-  friend class graph;
-
-private:
-  /* node list */
-  std::vector<node*> nodes;
-
-  /* position of the node with the zero name */
-  int zero_index;
-
-public:
-  /* constructor */
-  graph_name(int size);
-  graph_name* copy();
-
-  /* comparison tools */
-  bool equal(graph_name* other);
-
-  /* split and merge */
-  void split(int i);
-  void merge(int i);
-
-  /* debuging */
-  void print();
-
-} graph_name;

### 2021-06-02 v2/main.cpp

@@ -1,186 +1,0 @@
-#include <ctime>
-
-#include "node.hpp"
-
-#include "node_public.inl"
-#include "node_private.inl"
-#include "node_debug.inl"
-
-#include "graph_names.hpp"
-
-#include "graph_names_public.inl"
-#include "graph_names_debug.inl"
-
-#include "graph.hpp"
-
-#include "graph_public.inl"
-#include "graph_private.inl"
-#include "graph_debug.inl"
-
-#include "rules.inl"
-
-void print_vector(std::vector<int> &vect) {
-  for (auto it = vect.begin(); it < vect.end(); ++it)
-    printf("%d ", *it);
-  printf("\n");
-}
-
-int main() {
-  std::srand(std::time(nullptr));
-
-  /*graph* g = new graph(20);
-  g->randomize(5, 5);
-
-  std::vector<int> split_nodes;
-  std::vector<int> merge_nodes;
-
-  for (int i = 0; i < 20; i++) {
-    g->step_all();
-
-    g->print();
-
-    get_split(g, split_nodes);
-    get_merge(g, merge_nodes);
-    g->split_merge(split_nodes, merge_nodes);
-
-
-    print_vector(split_nodes);
-    print_vector(merge_nodes);
-
-    g->print();
-    g->print_name();
-    printf("\n");
-  } */
-
-  for (int j = 0; j < 100; j++) {
-    graph* g = new graph(20);
-    g->randomize(5, 5);
-
-    std::vector<int> split_nodes;
-    std::vector<int> merge_nodes;
-
-    for (int i = 0; i < 500; i++) {
-      //test
-      //-------------------------------
-      graph* g2 = g->copy();
-
-      g->print();
-      g->print_name();
-
-      printf("\n");
-
-      get_split(g2, split_nodes);
-      get_merge(g2, merge_nodes);
-
-      printf("split at "); print_vector(split_nodes);
-      printf("merge at "); print_vector(merge_nodes);
-
-      g2->split_merge(split_nodes, merge_nodes);
-
-      g2->print();
-      g2->print_name();
-
-      printf("\n");
-
-      get_split(g2, split_nodes);
-      get_merge(g2, merge_nodes);
-      g2->split_merge(split_nodes, merge_nodes);
-
-      if (!g->equal(g2)) {
-        printf("\n---------------------------\nerror:%d\n---------------------------\n\n", i);
-        g->print();
-        g->print_name();
-
[…]

### 2021-06-02 v2/node.hpp

@@ -1,49 +1,0 @@
-#pragma once
-#include <vector>
-
-#define EMPTY_ELLEMENT -1
-
-typedef class node {
-private:
-  /* list describing the node */
-  /*std::vector<int> names;
-  std::vector<int> bracket_depth;
-  std::vector<int> immediate_left_bracket;*/
-
-  /* presence and position of the name zero */
-  bool countains_zero_;
-  int zero_idx;
-
-  /* split index */
-  bool split_index_calculated = false;
-  int split_index;
-  void calculate_split_index();
-
-  /* copy up to an index */
-  node* copy(int start, int end);
-
-  /* empty depth */
-  bool _is_empty();
-  int _empty_depth();
-
-public:
-  /* list describing the node */
-  std::vector<int> names;
-  std::vector<int> bracket_depth;
-  std::vector<int> immediate_left_bracket;
-  /* constructor and destructor */
-  node(int idx);
-  node* copy();
-
-  /* comparison tools */
-  bool countains_zero();
-  bool equal(node* other);
-
-  /* merge and split */
-  void merge_right(node* right);
-  node* right();
-  void set_left();
-
-  /* debuging function */
-  void print();
-} node;

### 2021-06-02 v3/classical/graph.hpp

@@ -1,363 +1,0 @@
-#pragma once
-
-#include "graph_name.hpp"
-#include <vector>
-#include <stdio.h>
-#include <utility> //for pairs
-#include <random>
-#include <chrono>
-#include <algorithm>    // std::rotate
-
-/* forward declaration of the graph_t type */
-typedef class graph graph_t;
-
-class graph {
-private:
-	/* variables */
-	graph_name_t* name_;
-	std::vector<unsigned int> left_;
-	std::vector<unsigned int> right_;
-
-	/* useful functions */
-	void overflow_left(std::vector<unsigned int>& pos);
-	void overflow_right(std::vector<unsigned int>& pos);
-	void rotate_once_left(std::vector<unsigned int>& pos);
-	void rotate_once_right(std::vector<unsigned int>& pos);
-
-public:
-	/* normal constructors */
-	graph(int n) {
-		name_ = new graph_name(n);
-	}
-
-	graph(int n, std::vector<unsigned int> &left, std::vector<unsigned int> &right) : left_(left), right_(right) {
-		name_ = new graph_name(n);
-	}
-
-	/* size operator */
-	size_t inline size() {
-		return name_->size();
-	}
-
-	/* copy opperator */
-	graph_t inline *copy() {
-		/* just copy the vectors */
-		graph_t* this_copy = new graph(0);
-		this_copy->name_ = name_->copy();
-		this_copy->left_ = left_;
-		this_copy->right_ = right_;
-
-		/* save memory */
-		left_.shrink_to_fit();
-		right_.shrink_to_fit();
-	
-		return this_copy;
-	}
-
-	/* getters */
-	std::vector<unsigned int> inline const &left() const { return left_; };
-	std::vector<unsigned int> inline const &right() const { return right_; };
-	graph_name_t inline const *name() const { return name_; };
-
-
-	/* randomizer */
-	void randomize(unsigned int n);
-	void randomize();
-
-	/* for debuging */
-	void print();
-
-	/* comparators */
-  	bool inline equal(graph_t* other);
-
-  	/* split and merge */
-  	/* split_merge type enum */
-  	typedef enum split_merge_type {
-		split_t,
-		merge_t,
-	} split_merge_type_t;
-	/* typedef of the pair of an index and a split_merge_type */
-  	typedef std::pair<unsigned int, split_merge_type_t> split_merge_t;
-  	/* functions */
[…]

### 2021-06-02 v3/classical/graph_name.hpp

@@ -1,138 +1,0 @@
-#pragma once
-
-#include "node.hpp"
-#include <vector>
-#include <stdio.h>
-
-/* forward declaration of the graph_t type */
-typedef class graph_name graph_name_t;
-
-/* graph class */
-class graph_name {
-private:
-	/* node list */
-	std::vector<node_t*> nodes_;
-
-public:
-	/* normal constructors */
-	graph_name(unsigned int size) {
-		for (int i = 0; i < size; ++i)
-			nodes_.push_back(new node(i));
-	}
-
-	/* size operator */
-	size_t inline size() {
-		return nodes_.size();
-	}
-
-	/* getter */
-	std::vector<node_t*> inline const &nodes() {
-		return nodes_;
-	}
-
-	/* copy opperator */
-	graph_name_t inline *copy() {
-		/* just copy the vector */
-		graph_name_t* this_copy = new graph_name(0);
-		this_copy->nodes_ = nodes_; // !! should check copy !!
-		return this_copy;
-	}
-
-	/* for debuging */
-	void print();
-
-	/* comparators */
-  	bool inline equal(const graph_name* other) const;
-
-  	/* split and merge */
-  	bool inline split(unsigned int idx);
-  	void inline merge(unsigned int idx);
-};
-
-/* comparator */
-bool graph_name::equal(const graph_name* other) const {
-	/* check if size match */
-	if (nodes_.size() != other->nodes_.size())
-		return false;
-
-	/* iterate through node names */
-	auto this_it = nodes_.begin();
-	auto other_it = other->nodes_.begin();
-
-	while(this_it < nodes_.end()) {
-		/* compare each node pair */
-		if (!(*this_it)->equal(*other_it))
-			return false;
-
- 	    ++this_it; ++other_it;
-	}
-
-	return true;
-}
-
-/* split */
-bool graph_name::split(unsigned int idx) {
-	/* if the node isn't the first */
-	if (idx > 0) {
-		/* add new node */
-		nodes_.insert(nodes_.begin() + idx + 1, nodes_[idx]->right());
-
-		/* replace old node */
-		nodes_[idx] = nodes_[idx]->left();
-
-		/* no need to rotate */
-		return false;
-	}
-	
-	/* new nodes_ */
-	node_t* left = nodes_[idx]->left();
-	node_t* right = nodes_[idx]->right();
-
-	if (left->has_most_left_zero()) {
[…]

### 2021-06-02 v3/classical/node.hpp

@@ -1,187 +1,0 @@
-#pragma once
-
-#include <stdio.h>
-
-/* forward declaration of the node_t type */
-typedef class node node_t;
-
-/* node class */
-class node {
-private:
-  /* node type enum */
-	typedef enum node_type {
-		element_t,
-		pair_t,
-		left_t,
-		right_t,
-	} node_type_t;
-
-	/* type and node variables */
-	node_type_t type;
-	int element_;
-	node_t* left_right_;
-	node_t* left_;
-	node_t* right_;
-	bool _has_most_left_zero = false;
-
-	/* private constructor */
-	node(node_t* left_right) : left_right_(left_right) {}
-
-	/* for debuging */
-	void print_w_paraenthesis();
-public:
-	/* normal constructors */
-	node(node_t* left, node_t* right);
-	node(int n) : element_(n) {
-		type = element_t;
-		_has_most_left_zero = n == 0;
-	}
-
-	/* copy opperator */
-	node_t inline*copy() {
-		/* no need to copy here (: */
-		return this;
-	}
-
-	/* for debuging */
-	void print();
-
-	/* comparators */
-	bool inline equal(node_t* other);
-	bool inline const &has_most_left_zero() { return _has_most_left_zero; }
-
-	/* split */
-	node_t* left();
-	node_t* right();
-};
-
-/* comparator */
-bool node::equal(node_t* other) {
-	/* check if types match */
-	if (type != other->type)
-		return false;
-
-	switch(type) {
-		case element_t:
-		{
-			return element_ == other->element_;
-		}
-
-		case pair_t:
-		{
-			return left_->equal(other->left_) && right_->equal(other->right_);
-		}
-
-		default:
-		{
-			return left_right_->equal(other->left_right_);
-		}
-	}
-}
-
-/* debuging */
-void node::print_w_paraenthesis() {
-	switch(type) {
-		case element_t:
-		{
-			printf("%d", element_);
-			return;
-		}
-
-		case pair_t:
-		{
-			printf("(");
-			left_->print_w_paraenthesis();
-			printf("∧");
-			right_->print_w_paraenthesis();
-			printf(")");
-			return;
-		}
-
-		case left_t:
-		{
-			left_right_->print_w_paraenthesis();
-			printf(".l");
-			return;
-		}
-
-		default:
-		{
-			left_right_->print_w_paraenthesis();
-			printf(".r");
-			return;
-		}
-	}
-}
-
-void node::print() {
[…]

### 2021-06-02 v3/classical/rules.hpp

@@ -1,135 +1,0 @@
-#pragma once
-
-#include "graph.hpp"
-#include <stdio.h>
-#include <utility> //for pairs
-#include <vector>
-
-/* function to get all split and merges */
-std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
-	std::vector<graph::split_merge_t> split_merge;
-
-	if (graph->left().size() == 0 ||
-	graph->right().size() == 0)
-		return split_merge;
-
-	auto last_left = graph->left().end() - 1;
-	auto last_right = graph->right().end() - 1;
-	unsigned int last_idx = graph->size() - 1;
-
-	auto left_it = graph->left().begin();
-	auto right_it = graph->right().begin();
-	bool first_or_last_split = *left_it == *right_it && *left_it == 0;
-	while (true) {
-		/* check if there are any particules left after iterating */
-		if (right_it > last_right ||
-		left_it > last_left)
-			break;
-
-		if (*left_it == *right_it) {
-			/* check for split */
-			split_merge.push_back(std::pair<unsigned int, graph::split_merge_type_t>((*left_it), graph->split_t));
-
-			/* check for last split */
-			if (*right_it == last_idx)
-				first_or_last_split = true;
-
-			++right_it;
-			++left_it;
-		} else if (*left_it < *right_it) {
-			/* chedk for merges */
-			if (*left_it == *right_it - 1)
-				if (left_it == last_left) {
-					split_merge.push_back(std::pair<unsigned int, graph::split_merge_type_t>((*left_it), graph->merge_t));
-				} else if (*(left_it + 1) != *right_it)
-					split_merge.push_back(std::pair<unsigned int, graph::split_merge_type_t>((*left_it), graph->merge_t));
-
-			++left_it;
-		} else
-			++right_it;
-	}
-		
-	if (!first_or_last_split)
-		if (*last_left == last_idx &&
-		graph->right()[0] == 0)
-			split_merge.push_back(std::pair<unsigned int, graph::split_merge_type_t>(last_idx, graph->merge_t));
-
-	return split_merge;
-}
-
-/* to check */
-bool inline graph_checker(graph_t* graph) {
-	int size = graph->size();
-
-	if (graph->left()[0] < 0)  {
-		printf("\nparticules going left 0 > %d\n", graph->left()[0]);
-		return false;
-	}
-
-	if (graph->left()[0] >= size) {
[…]

### 2021-06-02 v3/quantum/checks.hpp

@@ -1,10 +1,0 @@
-#pragma once
-
-#include <vector>
-#include <complex> //for complex
-#include "state.hpp"
-#include "rules.hpp"
-
-bool check(state_t* s) {
-	return true;
-}

### 2021-06-02 v3/quantum/rules.hpp

@@ -1,60 +1,0 @@
-#pragma once
-
-#include <vector>
-#include <math.h>  //pow
-#include <utility> //for pairs
-#include <complex> //for complex
-#include "../classical/graph.hpp"
-
-const double double_tolerance = 0; //1e-32;
-
-/* count the number of subsets */
-template<class T>
-int num_subset(std::vector<T> const &vect) {
-	return pow(2, vect.size());
-}
-
-/* create a subset and a probability from the subset indice */
-std::pair<std::vector<graph::split_merge_t>, std::complex<double>> subset(std::vector<graph::split_merge_t>& split_merge, int subset_numb,
-	std::complex<double> non_merge, std::complex<double> non_split, std::complex<double> merge, std::complex<double> split) {
-	
-	std::vector<graph::split_merge_t> res;
-	std::complex<double> proba = 1;
-
-	for (int i = 0; i < split_merge.size(); ++i) {
-		/* i_th bit of subset_numb */
-		if (subset_numb%2) {
-			/* add opperation to res */
-			res.push_back(split_merge[i]);
-
-			/* get proba */
-			if (split_merge[i].second) {
-				proba *= split;
-			} else
-				proba *= merge;
-		} else
-			if (split_merge[i].second) {
-				proba *= non_split;
-			} else
-				proba *= non_merge;
-
-
-		subset_numb /= 2;
-	}
-
-	return std::pair<std::vector<graph::split_merge_t>, std::complex<double>>(res, proba);
-}
-
-std::pair<std::vector<graph::split_merge_t>, std::complex<double>> subset(std::vector<graph::split_merge_t>& split_merge, int subset_numb,
-	double teta, double phi) {
-
-	/* compute amplitudes */
-	std::complex<double> non_split = std::cos(teta);
-	std::complex<double> non_merge = -std::cos(teta);
-
-	double r = std::sin(teta);
-	std::complex<double> merge = std::polar(r, phi);
-	std::complex<double> split = std::polar(r, -phi);
-
-	return subset(split_merge, subset_numb, non_merge, non_split, merge, split);
-}

### 2021-06-02 v3/quantum/state.hpp

@@ -1,212 +1,0 @@
-#pragma once
-
-#include <vector>
-#include <utility>
-#include <complex> //for complex
-#include "../classical/graph.hpp"
-#include "../classical/rules.hpp"
-#include "rules.hpp"
-
-// forward definition of the state type
-typedef class state state_t;
-
-class state {
-public:
-	// type definition 
-	typedef std::pair<graph_t*, std::complex<double>> graph_w_proba_t;
-
-private:
-	// main list 
-	std::vector<graph_w_proba_t> graphs_;
-
-	// parameters 
-	std::complex<double> non_split_ = 1;
-	std::complex<double> non_merge_ = -1;
-	std::complex<double> merge_ = 0;
-	std::complex<double> split_ = 0;
-
-	//comparator
-	bool quick_greater(graph_t* g1, graph_t* g2) {
-		if (g1->left() > g2->left())
-			return true;
-
-		if (g1->left() < g2->left())
-			return false;
-
-		return g1->right() > g2->right();
-	}
-
-	// checker
-	friend bool check(state_t* s);
-
-public:
-	// single graph constructor 
-	state(graph_t* g) {
-		// add graph 
-		graphs_.push_back(std::pair<graph_t*, std::complex<double>>(g, std::complex<double>(1, 0)));
-	}
-
-	// setter 
-	void set_params(double teta, double phi) {
-		// compute amplitude 
-		non_split_ = std::cos(teta);
-		non_merge_ = -non_split_;
-
-		double r = std::sin(teta);
-		merge_ = std::polar(r, phi);
-		split_ = std::polar(r, -phi);
-	}
-
-	// getters 
-	std::vector<graph_w_proba_t> inline const &graphs() { return graphs_; }
-
-	// insert operators 
-	void inline insert_temp(graph_t* g, std::complex<double> proba) {
-		std::pair<graph_t*, std::complex<double>> G(g, proba);
-		graphs_.push_back(G);
-	}
-	void sort_and_reduce();
-
-	// dynamic 
-	void step_all();
-	void split_merge_all();
-
-	// for debugging 
-	void print();
-};
-
-// insert operators 
-void state::sort_and_reduce() {
-	auto greater_than = [&] (graph_w_proba_t a, graph_w_proba_t b) {
-		return quick_greater(a.first, b.first);
-	};
-
-	int blocks = 1;
-	int size = graphs_.size();
-
[…]

### 2021-06-02 v3/tests/classic_test.cpp

@@ -1,27 +1,0 @@
-#include "../classical/rules.hpp"
-#include "../classical/graph.hpp"
-#include <stdio.h>
-
-int main() {
-  for (int j = 0; j < 7; ++j) {
-    graph_t* g = new graph(50);
-
-    g->randomize(20);
-
-    if (!graph_checker(g))
-      return -1;
-
-    printf("%lu", g->size());
-
-    for (int i = 0; i < 5000000; ++i) {
-      g->step();
-
-      auto split_merge = get_split_merge(g);
-      g->split_merge(split_merge);
-
-      printf(",%lu", g->size());
-    }
-    if (j < 6)
-      printf(";");
-  }
-}

### 2021-06-02 v3/tests/graph_name_test.cpp

@@ -1,29 +1,0 @@
-#include "../classical/graph_name.hpp"
-#include <stdio.h>
-
-int main() {
-  graph_name_t* n_1 = new graph_name(6);
-  printf("*new graph_name(6): "); n_1->print();
-
-  graph_name_t* n_2 = n_1->copy();
-
-  n_1->merge(5);
-  printf("\nmerge 5:            "); n_1->print();
-
-  n_1->split(3);
-  printf("\nsplit 3:            "); n_1->print();
-
-  n_1->split(0);
-  printf("\nsplit 0:            "); n_1->print();
-
-  printf("\ncopy*:              "); n_2->print();
-
-  n_1->merge(3);
-  printf("\nmerge 3:            "); n_1->print();
-
-  if (n_1->equal(n_2)) {
-     printf("\ninitial copy equal to previous graph\n");
-  } else {
-    printf("\ninitial copy not equal to previous graph\n");
-  }
-}

### 2021-06-02 v3/tests/injectivity_test.cpp

@@ -1,28 +1,0 @@
-#include "../classical/rules.hpp"
-#include "../classical/graph.hpp"
-#include <stdio.h>
-
-int main() {
-  graph_t* g = new graph(20);
-
-  for (int i = 0; i < 10000; ++i) {
-    g->randomize();
-    graph_t* c = g->copy();
-
-    auto split_merge = get_split_merge(g);
-    g->split_merge(split_merge);
-
-    split_merge = get_split_merge(g);
-    g->split_merge(split_merge);
-
-    if (!g->equal(c)){
-      c->print(); printf("\n");
-      g->print(); printf("\n");
-      return -2;
-    }
-
-    if (!graph_checker(g))
-      return -1;
-  }
-  printf("\n");
-}

### 2021-06-02 v3/tests/node_test.cpp

@@ -1,27 +1,0 @@
-#include "../classical/node.hpp"
-#include <stdio.h>
-
-int main() {
-  node_t* n_1 = new node(1);
-  printf("new node(1): "); n_1->print();
-
-  node_t* n_1_l = n_1->left();
-  printf("\n.l:          "); n_1_l->print();
-
-  node_t* n_1_r = n_1->right();
-  printf("\n.r:          "); n_1_r->print();
-
-  node_t* n_1_r_l = new node(n_1_r, n_1_l);
-  printf("\n.r∧.l:       "); n_1_r_l->print();
-
-  node_t* n_1_l_r = new node(n_1_l, n_1_r);
-  printf("\n.l∧.r:       "); n_1_l_r->print();
-
-  if (n_1->equal(n_1_l_r)) {
-    printf("\n1 == 1.l∧1.r");
-  } else {
-    printf("\n1 != 1.l∧1.r");
-  }
-
-  printf("\ndo pointer match (for 1 and 1.l∧1.r): %p != %p\n", n_1_l_r, n_1);
-}

### 2021-06-02 v3/tests/quantum_speed_test.cpp

@@ -1,30 +1,0 @@
-#include "../classical/rules.hpp"
-#include "../classical/graph.hpp"
-#include "../quantum/rules.hpp"
-#include "../quantum/state.hpp"
-#include "../quantum/checks.hpp"
-#include <stdio.h>
-
-#define _USE_MATH_DEFINES
-#include <cmath>
-
-int main() {
-    graph_t* g_1 = new graph(6);
-    g_1->randomize();
-
-    state_t* s = new state(g_1);
-	s->set_params(M_PI_4, 0);
-
-    for (int i = 1;; ++i) {
-    	#ifdef TEST
-    	if (check(s))
-    		return -1;
-    	#endif
-
-    	printf("%ld graphs at the %dth iteration\n", s->graphs().size(), i);
-
-    	printf("\nsplit_merge_all() ...\n"); s->split_merge_all();
-    	printf("step_all() ...\n"); s->step_all();
-		  printf("sort_and_reduce() ...\n\n"); s->sort_and_reduce(); printf("\n");
-   	}
-}

### 2021-06-02 v3/tests/state_test.cpp

@@ -1,86 +1,0 @@
-#include "../classical/rules.hpp"
-#include "../classical/graph.hpp"
-#include "../quantum/rules.hpp"
-#include "../quantum/state.hpp"
-#include "../quantum/checks.hpp"
-#include <stdio.h>
-#include <math.h> //pow cos sin and sqrt
-#include <complex>
-
-
-#define _USE_MATH_DEFINES
-#include <cmath>
-
-int main() {
-	printf("A graphs is inputed by a series of ndoes, having particules (`>` for right and `<` for left) or not.\n");
-	printf("With nodes being separated by a '-'.\n");
-	printf("you can also input 'r' to create a random graph of size 6\n");
-	printf("For exemple the graph:\n    >-<>--<\nis read as:\n    -| |0|>|--|<|1|>|--| |2| |--|<|3| |-\n");
-
-	while (true) {
-		printf("\n----------------------------------------------------\n\nPleas enter next graph (Ctrl+C to exit):\n");
-
-		std::vector<unsigned int> left, right;
-		graph_t* g_1;
-		int n = 0;
-
-		while (true) {
-			switch (std::getchar()) {
-				case '<':
-					left.push_back(n);
-					break;
-
-				case '>':
-          			right.push_back(n);
-          			break;
-
-        		case '-':
-          			++n;
-          			break;
-
-        		case '\n':
-          			++n;
-          			goto read;
-
-        		case 'r':
-        			while(std::getchar() != '\n') { }
-          			goto random;
-
-        		default:
-          			return -1;
-      		}
-    	}
-
-read:
-    	g_1 = new graph(n, left, right);
-    	printf("\nread from input*: "); g_1->print();
-    	goto loop;
-
-random:
-    	g_1 = new graph(6);
-    	printf("new graph(6):  "); g_1->print();
-
-    	g_1->randomize();
-    	printf("\nrandomize()*:  "); g_1->print(); printf("\n");
-
-loop:
-
-		state_t* s = new state(g_1);
-		s->set_params(M_PI_4, M_PI_4);
-
-		s->split_merge_all();
-		s->sort_and_reduce();
-
-		printf("\nmerge_split():\n"); s->print();
-
-		s->split_merge_all();
-		s->sort_and_reduce();
-
-		printf("\n\nmerge_split():\n"); s->print();
-
-		if (check(s)) {
-			printf("\nstate is OK\n");
-		} else
-			printf("\nstate is not OK\n");
-	}
-}

### 2021-06-02 v4/quantum/state.hpp

@@ -139,6 +139,13 @@ void state::step_split_merge_all(bool step, bool split_merge, bool reversed) {
   		if (split_merge) {
   			auto split_merge = get_split_merge(graph);
 
+  			#pragma omp task
+  			{
+  				// update the probability of the graph without split or merge 
+				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
+				graphs_.insert({graph, mag * mag_no_split_merge});
+  			}
+
 			// add all graphs that actually have some split ot merge 
 			const int n_max = num_subset(split_merge);
 			#pragma omp taskloop
@@ -151,13 +158,10 @@ void state::step_split_merge_all(bool step, bool split_merge, bool reversed) {
 			  	//add graph
 			  	graphs_.insert({g_, mag * mag_split_merge});
 			}
-			// update the probability of the graph without split or merge 
-			auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
-			mag *= mag_no_split_merge;
-  		}
-  		
-  		//add graph
-		graphs_.insert({graph, mag});
+			
+  		} else
+	  		//add graph
+			graphs_.insert({graph, mag});
   	}
 }
 

### 2021-06-02 paper/paper.tex
optimized some loops, made the code more readable, and optimized memory usage A LOT

--- 2021-06-01 paper/paper.tex
@@
 
-Even including floating points errors, we can esaily do this test with around 5 steps, obtain around 200k graphs after the 5 forward iteration, and comme back to the same step within 0.001\% error in the magnitude.
+Even including floating points errors, we can esaily do this test with around 5 steps, obtain around 7M graphs after the 5 forward iteration, and comme back to the same step within $10^{-6}$ error in the magnitude.
 
@@
 		// add right node
-		nodes_.insert(nodes_.begin() + idx + 1,
-			node_t(buff_idx, node, point_r_idx));
+		nodes_.emplace(nodes_.begin() + idx + 1, buff_idx, node, point_r_idx);
 
@@
 	void split_merge(std::vector<split_merge_t>& split_merge) {
-		/* first check if there are any split or merges */
+		if (split_merge.empty())
+			return;
 
@@
 		// check for last merge
-		/* ... */
-		if (last_merge()) {
-			name_->merge(last_idx);
+		if (split_merge.back() == split_merge_t(size() - 1, merge_t)) {
+			name_->merge(size() - 1);
 			overflow_right(left_);	
 			split_merge.pop_back();
-			/* ... */
 		}
@@
 
-		// split and merge names 
 		// and calculating max displacement 
 		int total_displacement = 0;
-		for (auto split_merge_it = split_merge.rbegin(); split_merge_it != split_merge.rend(); ++split_merge_it)
-			if ((*split_merge_it).second == split_t) {
-				first_split |= name_->split((*split_merge_it).first) && (*split_merge_it).first == 0;
+		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
+			if (type == split_t) {
+				++total_displacement;
+			} else
+				--total_displacement;
 
-				++total_displacement;
-			} else {
-				name_->merge((*split_merge_it).first);
-				--total_displacement;
-			}
+		// reserve space for nodes
+		name_->reserve(total_displacement);
+
+		// split and merge names
+		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
+			if (type == split_t) {
+				first_split |= name_->split(pos);
+			} else
+				name_->merge(pos);
 
 		// move particules
+		auto const split_merge_begin = split_merge.rend();
 		int displacement = total_displacement;
-		auto split_merge_it = last_split_merge;
-		for (auto left_it = left_.rbegin(); left_it != left_.rend(); ++left_it) {
+		auto split_merge_it = split_merge.rbegin();
+		for (auto &left_it : left_ | std::ranges::views::reverse) {
 			// check if there are any nodes left
-			while (split_merge_it >= split_merge.begin()) {
+			for (;split_merge_it->first >= left_it && split_merge_it != split_merge_begin; ++split_merge_it)
 				// check if the node is split or merged
-				if ((*split_merge_it).first >= *left_it) {
-					if ((*split_merge_it).second == split_t) {
+				if (split_merge_it->second == split_t) {
 						--displacement; // decrement the displacement 
@@
 						++displacement; // decrement the displacement
-					--split_merge_it;
-				} else
+
+			//check if we can exit
+			if (split_merge_it == split_merge_begin && displacement == 0)
 				break;
 
+			left_it += displacement;
 		}
 
-			if (split_merge_it == split_merge.begin() && displacement == 0)
-				break;
-
-			*left_it += displacement;
-		}
-
-		/* we than do the exact same thing with particule going to the right, rplacing ">=" at line 48 by a ">" */
+		/* we than do the exact same thing with particule going to the right, rplacing ">=" at line 42 by a ">" */
 
@@
 	std::vector<graph::split_merge_t> split_merge;
-
-	/* first check if there are any particules to check */
 
@@
 \begin{lstlisting}[style=CStyle]
+	//...
+	void reduce_all() {
+		for(auto it = graphs_.begin(); it != graphs_.end();) {
+			// range of similar graphs to delete
+			auto upper = graphs_.equal_range(it->first).second;
+
+			for(auto jt = std::next(it); jt != upper; ++jt)
+		    	it->second += jt->second;
+
+			// if the first graphgs has a zero probability, erase the whole range
+			if (!check_zero(it->second))
+				++it;
+
+			it = graphs_.unsafe_erase(it, upper);
+		}
+	}
+	//...
 \end{lstlisting}
@@
 \begin{lstlisting}[style=CStyle]
+	//...
+	void step_split_merge_all() {
+		graph_map_t buff;
+		buff.swap(graphs_);
+
+		#pragma omp parallel
+		#pragma omp single
+		for (auto & [graph, mag] : buff)
+		#pragma omp task
+	  	{
+
+	  		graph->step(); //not present for reversed_split_merge_step_all()
+
+	  		auto split_merge = get_split_merge(graph);
+
+	  		#pragma omp task
+	  		{
+	  			// update the probability of the graph without split or merge 
+				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
+
+				// copy and graph->reversed_step() befor insert for reversed_split_merge_step_all()
+				graphs_.insert({graph, mag * mag_no_split_merge});
+	  		}
+
+	  		// add all graphs that actually have some split ot merge 
+	  		const int n_max = num_subset(split_merge);
+	  		for (int j = 1; j < n_max; ++j)
+	  		#pragma omp task
+	  		{
+	  			graph_t* g_ = graph->copy();
+
+	  			auto [split_merge_list, mag_split_merge] = subset(split_merge, j, non_merge_, merge_);
+
+	  			// graph->reversed_step() befor insert for reversed_split_merge_step_all()
+	  			g_->split_merge(split_merge_list);
+
+	  			//add graph
+	  			graphs_.insert({g_, mag * mag_split_merge});
+	  		}
+	  	}
+	}
+	//...
 \end{lstlisting}

### 2021-06-02 v4/classical/graph.hpp

@@ -8,6 +8,7 @@
 #include <chrono>
 #include <algorithm>    // std::rotate
 #include <boost/functional/hash.hpp>
+#include<ranges>
 
 // forward declaration of the graph_t type 
 typedef class graph graph_t;
@@ -177,88 +178,75 @@ void graph::rotate_once_right(std::vector<unsigned int>& pos) {
 
 // split merge 
 void graph::split_merge(std::vector<split_merge_t>& split_merge) {
-	if (left_.size() == 0 ||
-	right_.size() == 0 ||
-	split_merge.size() == 0)
+	if (split_merge.empty())
 		return;
 	
 	hashed_ = false;
 
-	// check for last merge 
-	auto last_split_merge = split_merge.end() - 1;
-	int last_idx = size() - 1;
-	if ((*last_split_merge).first == last_idx &&
-	(*last_split_merge).second == merge_t) {
-		name_->merge(last_idx);
-
-		overflow_right(left_);
-		
+	// check for last merge
+	if (split_merge.back() == split_merge_t(size() - 1, merge_t)) {
+		name_->merge(size() - 1);
+		overflow_right(left_);	
 		split_merge.pop_back();
-
-		--last_split_merge;
-		--last_idx;
 	}
 		
 	// check for first element split 
 	bool first_split = false;
 
-	// split and merge names 
 	// and calculating max displacement 
 	int total_displacement = 0;
-	for (auto split_merge_it = split_merge.rbegin(); split_merge_it != split_merge.rend(); ++split_merge_it)
-		if ((*split_merge_it).second == split_t) {
-			first_split |= name_->split((*split_merge_it).first) && (*split_merge_it).first == 0;
-
+	for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
+		if (type == split_t) {
 			++total_displacement;
-		} else {
-			name_->merge((*split_merge_it).first);
+		} else
 			--total_displacement;
-		}
 
-	// move particules 
+	// reserve space for nodes
+	name_->reserve(total_displacement);
+
+	// split and merge names
+	for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
+		if (type == split_t) {
+			first_split |= name_->split(pos);
+		} else
+			name_->merge(pos);
+
+	// move particules
+	auto const split_merge_begin = split_merge.rend();
 	int displacement = total_displacement;
-	auto split_merge_it = last_split_merge;
[…]

### 2021-06-02 v4/classical/graph_name.hpp

@@ -12,8 +12,8 @@ class graph_name {
 private:
 	// node list 
 	std::vector<node_t> nodes_;
-	std::vector<node_t> node_buff_;
-	std::vector<int> trash_collection_;
+	std::vector<node_t> mutable node_buff_;
+	std::vector<int> mutable trash_collection_;
 
 	// hash
 	size_t mutable hash_ = 0;
@@ -35,11 +35,20 @@ public:
 	// normal constructors 
 	graph_name(unsigned int size) {
 		for (int i = 0; i < size; ++i)
-			nodes_.push_back(node(i));
+			nodes_.emplace_back(i);
 	}
 
 	// getters
 	std::vector<node_t> const &nodes() const { return nodes_; }
+
+	// memory managment
+	void inline reserve(int Dsize) {
+		if (Dsize > 0) {
+			nodes_.reserve(size() + Dsize);
+		} else
+			nodes_.shrink_to_fit();
+		
+	}
 
 	// size operator 
 	size_t inline size() const {
@@ -65,6 +74,10 @@ public:
 	size_t inline hash() const {
 		if (hashed_)
 			return hash_;
+
+		// memory managment at hashing time
+		trash_collection_.shrink_to_fit();
+		node_buff_.shrink_to_fit();
 
 		hash_ = 0;
 
@@ -115,8 +128,7 @@ bool inline graph_name::split(unsigned int idx) {
 	nodes_[idx] = node_t(buff_idx, node, point_l_idx);
 
 	// add right node
-	nodes_.insert(nodes_.begin() + idx + 1,
-		node_t(buff_idx, node, point_r_idx));
+	nodes_.emplace(nodes_.begin() + idx + 1, buff_idx, node, point_r_idx);
 	
 	return false;
 }

### 2021-06-02 v4/classical/rules.hpp

@@ -9,10 +9,6 @@
 std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
 	std::vector<graph::split_merge_t> split_merge;
 
-	if (graph->left().size() == 0 ||
-	graph->right().size() == 0)
-		return split_merge;
-
 	auto last_left = graph->left().end() - 1;
 	auto last_right = graph->right().end() - 1;
 	unsigned int last_idx = graph->size() - 1;

### 2021-06-02 v4/quantum/state.hpp

@@ -69,10 +69,7 @@ public:
 	void inline step_split_merge_all() { step_split_merge_all(true, true, false); }
 	void inline step_all() { step_split_merge_all(true, false, false); }
 	void inline split_merge_all() { step_split_merge_all(false, true, false); }
-	void inline reversed_split_merge_step() {
-		split_merge_all();
-		step_split_merge_all(false, false, true);
-	}
+	void inline reversed_split_merge_step() { step_split_merge_all(false, true, true); }
 
 	// for debugging 
 	void print();
@@ -86,17 +83,16 @@ void state::reduce_all() {
 
     for(auto it = graphs_.begin(); it != graphs_.end();) {
     	// range of similar graphs to delete
-    	auto range = graphs_.equal_range(it->first);
-    	auto start = range.first;
+    	auto upper = graphs_.equal_range(it->first).second;
 
-    	for(auto jt = std::next(it); jt != range.second; ++jt)
+    	for(auto jt = std::next(it); jt != upper; ++jt)
         	it->second += jt->second;
 
     	// if the first graphgs has a zero probability, erase the whole range
     	if (!check_zero(it->second))
-    		++start;
-
-    	it = graphs_.unsafe_erase(start, range.second);
+    		++it;
+    	
+    	it = graphs_.unsafe_erase(it, upper);
     }
 }
 
@@ -133,9 +129,6 @@ void state::step_split_merge_all(bool step, bool split_merge, bool reversed) {
   		if (step)
   			graph->step();
 
-  		if (reversed)
-  			graph->reversed_step();
-
   		if (split_merge) {
   			auto split_merge = get_split_merge(graph);
 
@@ -143,17 +136,29 @@ void state::step_split_merge_all(bool step, bool split_merge, bool reversed) {
   			{
   				// update the probability of the graph without split or merge 
 				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
-				graphs_.insert({graph, mag * mag_no_split_merge});
+
+				// need to copy the graph if we do the reversed step
+				if(reversed) {
+					graph_t* g_ = graph->copy();
+					g_->reversed_step();
+					graphs_.insert({g_, mag * mag_no_split_merge});
+				} else
+					graphs_.insert({graph, mag * mag_no_split_merge});
+				
   			}
 
 			// add all graphs that actually have some split ot merge 
[…]

### 2021-06-02 v4/tests/classical_injectivity_test.cpp

@@ -4,7 +4,11 @@
 #include <stdio.h>
 
 int main() {
-  for (int j = 0; j < 1000; ++j) {
+  #pragma omp parallel
+  #pragma omp single
+  for (int j = 0; j < 1000; ++j)
+  #pragma omp task
+  {
     
     graph_t* g = new graph(10);
 
@@ -26,11 +30,11 @@ int main() {
       if (c2->hash() != c->hash() /*!g->equal(c)*/){
         c2->print(); printf("\n");
         c->print(); printf("\n");
-        return -2;
+        throw;
       }
 
       if (!graph_checker(g))
-        return -1;
+        throw;
     }
   }
     

### 2021-06-02 v4/tests/quantum_injectivity_test.cpp

@@ -74,10 +74,12 @@ loop:
 			s->step_split_merge_all();
 			s->reduce_all();
 
-			if (check(s)) {
-				printf("\nstate is OK\n");
-			} else
-				printf("\nstate is not OK\n");
+			#ifdef TEST
+				if (check(s)) {
+					printf("\nstate is OK\n");
+				} else
+					printf("\nstate is not OK\n");
+			#endif
 		}
 		
 		if (n_iter <= 2) {
@@ -91,10 +93,12 @@ loop:
 			s->reversed_split_merge_step();
 			s->reduce_all();
 
-			if (check(s)) {
-				printf("\nstate is OK\n");
-			} else
-				printf("\nstate is not OK\n");
+			#ifdef TEST
+				if (check(s)) {
+					printf("\nstate is OK\n");
+				} else
+					printf("\nstate is not OK\n");
+			#endif
 		}
 
 		printf("\nafter %d reversed_merge_split_step():\n", n_iter); s->print();

### 2021-06-02 v4/tests/quantum_iteration.cpp

@@ -18,7 +18,7 @@ int main() {
     state_t* s = new state(g_1);
 	s->set_params(M_PI_4, M_PI_2);
 
-    for (int i = 1; i < 10; ++i) {
+    for (int i = 1; i < 11; ++i) {
 
         auto [avg, std_dev] = s->size_stat();
         printf("%ld graph of size %Lf±%Lf at the %dth iteration\n", s->graphs().size(), avg, std_dev, i);

### 2021-06-02 paper/paper.tex
passed a rule function to the step function of the state class

@@
 std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
-	std::vector<graph::split_merge_t> split_merge;
+	std::vector<graph::op_t> split_merge;
 
-	/* definition of left_it, right_it, last_left, last_right ... */
+	unsigned int const last_idx = graph->size() - 1;
 
+	auto left_it = graph->left().begin();
+	auto right_it = graph->right().begin();
 	bool first_or_last_split = *left_it == *right_it && *left_it == 0;
-	while (true) {
-		/* check if there are any particules left after iterating */
-		if (right_it > last_right ||
-		left_it > last_left)
-			break;
+	first_or_last_split |= graph->left().back() == last_idx && graph->right().back() == last_idx;
 
+	while (right_it < right_end = graph->right().end() && left_it < graph->left().end())
 		if (*left_it == *right_it) {
-			/* check for split */
-			split_merge.push_back({(*left_it), graph->split_t});
-
-			/* check for last split */
-			if (*right_it == last_idx)
-				first_or_last_split = true;
+			// check for split
+			split_merge.push_back({*left_it, graph->split_t});
 
@@
 		} else if (*left_it < *right_it) {
-			/* chedk for merges */
+			// chedk for merges
 			if (*left_it == *right_it - 1)
-				if (left_it == last_left) {
-					split_merge.push_back({(*left_it), graph->merge_t});
+				if (left_it == graph->left().end() - 1) {
+					split_merge.push_back({*left_it, graph->merge_t});
 				} else if (*(left_it + 1) != *right_it)
-					split_merge.push_back({(*left_it), graph->merge_t});
+					split_merge.push_back({*left_it, graph->merge_t});
 
@@
 			++right_it;
-	}
 
 	if (!first_or_last_split)
-		if (*last_left == last_idx &&
-		graph->right()[0] == 0)
+		if (graph->left().back() == last_idx && graph->right()[0] == 0)
 			split_merge.push_back({last_idx, graph->merge_t});
@@
 
-\subsubsection{subset of splist and merges}
-
-We first need to know the number of possible graphs from the lists of splits and merges:
-
-\begin{lstlisting}[style=CStyle]
-template<class T>
-int num_subset(std::vector<T> const &vect) {
-	return pow(2, vect.size());
-}
-\end{lstlisting}
-
-We can then associate a number between 0 and "num\_subset" to a certain compositions of all the splits and merges (by seeing the nth binary ditgit of this number as enabling the nth split or merge) :
-
-\begin{lstlisting}[style=CStyle]
-std::pair<std::vector<graph::split_merge_t>, std::complex<long double>> subset(std::vector<graph::split_merge_t>& split_merge, int subset_numb,
-	std::complex<long double>& non_merge, std::complex<long double>& merge) {
-
-	std::vector<graph::split_merge_t> res;
-	std::complex<long double> proba = 1;
-
-	for (int i = 0; i < split_merge.size(); ++i) {
-		long double sign = 1 - 2*split_merge[i].second;
-
-		/* i_th bit of subset_numb */
-		if (subset_numb%2) {
-			/* add opperation to res */
-			res.push_back(split_merge[i]);
-
-			/* get proba */
-			proba *= std::complex<long double>(merge.real(), sign*merge.imag());
-		} else
-			proba *= sign*non_merge;
-
-		subset_numb /= 2;
-	}
-
-	return {res, proba};
-}
-\end{lstlisting}
-
 \subsubsection{reduce\_all()}
@@
 
-\subsubsection{step\_split\_merge\_all() and reversed\_split\_merge\_step\_all()}
+\subsubsection{step\_all()}
+
+We pass a function "rule" that returns a vector of graphs and magnitude obtained from a single graph.
 
@@
 	//...
-	void step_split_merge_all() {
+	void state::step_all(std::function<tbb::concurrent_vector<std::pair<graph_t*, std::complex<long double>>>(graph_t* g)> rule) {
 		graph_map_t buff;
@@
 		{
-
-	  		graph->step(); //not present for reversed_split_merge_step_all()
-
-	  		auto split_merge = get_split_merge(graph);
-
-	  		#pragma omp task
-	  		{
-	  			// update the probability of the graph without split or merge 
-				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
-
-				// copy and graph->reversed_step() befor insert for reversed_split_merge_step_all()
-				graphs_.insert({graph, mag * mag_no_split_merge});
-	  		}
-
-	  		// add all graphs that actually have some split ot merge 
-	  		const int n_max = num_subset(split_merge);
-	  		for (int j = 1; j < n_max; ++j)
-	  		#pragma omp task
-	  		{
-	  			graph_t* g_ = graph->copy();
-
-	  			auto [split_merge_list, mag_split_merge] = subset(split_merge, j, non_merge_, merge_);
-
-	  			// graph->reversed_step() befor insert for reversed_split_merge_step_all()
-	  			g_->split_merge(split_merge_list);
-
-	  			//add graph
-	  			graphs_.insert({g_, mag * mag_split_merge});
-	  		}
+			auto graphs = rule(graph);
+			for (auto & [graph_, mag_] : graphs)
+			#pragma task
+	  			graphs_.insert({graph_, mag_ * mag});
 		}
@@
 	//...
+}
 \end{lstlisting}

### 2021-06-02 v4/classical/checks.hpp

@@ -9,17 +9,17 @@
 bool inline graph_checker(graph_t* graph) {
 	int size = graph->size();
 
-	if (graph->left()[0] < 0)  {
-		printf("\nparticules going left 0 > %d\n", graph->left()[0]);
+	if (graph->left[0] < 0)  {
+		printf("\nparticules going left 0 > %d\n", graph->left[0]);
 		return false;
 	}
 
-	if (graph->left()[0] >= size) {
-		printf("\nparticules going left %d >= %d\n", graph->left()[0], size);
+	if (graph->left[0] >= size) {
+		printf("\nparticules going left %d >= %d\n", graph->left[0], size);
 		return false;
 	}
 
-	for (auto it = graph->left().begin() + 1; it < graph->left().end(); ++it) {
+	for (auto it = graph->left.begin() + 1; it < graph->left.end(); ++it) {
 		if (*it <= *(it - 1)) {
 			printf("\nparticules going left unsorted %d <= %d\n", *it, *(it - 1));
 			return false;
@@ -36,17 +36,17 @@ bool inline graph_checker(graph_t* graph) {
 		}
 	}
 
-	if (graph->right()[0] < 0)  {
-		printf("\nparticules going right 0 > %d\n", graph->right()[0]);
+	if (graph->right[0] < 0)  {
+		printf("\nparticules going right 0 > %d\n", graph->right[0]);
 		return false;
 	}
 
-	if (graph->right()[0] >= size) {
-		printf("\nparticules going right %d > %d\n", graph->right()[0], size);
+	if (graph->right[0] >= size) {
+		printf("\nparticules going right %d > %d\n", graph->right[0], size);
 		return false;
 	}
 
-	for (auto it = graph->right().begin() + 1; it < graph->right().end(); ++it)
+	for (auto it = graph->right.begin() + 1; it < graph->right.end(); ++it)
 		if (*it <= *(it - 1) || *it < 0 || *it >= size) {
 			if (*it <= *(it - 1)) {
 				printf("\nparticules going right unsorted %d <= %d\n", *it, *(it - 1));

### 2021-06-02 v4/classical/graph.hpp

@@ -18,8 +18,6 @@ class graph {
 private:
 	// variables 
 	graph_name_t* name_;
-	std::vector<unsigned int> left_;
-	std::vector<unsigned int> right_;
 
 	// hash
 	size_t mutable hash_ = 0;
@@ -32,12 +30,15 @@ private:
 	void rotate_once_right(std::vector<unsigned int>& pos);
 
 public:
+	std::vector<unsigned int> left;
+	std::vector<unsigned int> right;
+
 	// normal constructors 
 	graph(int n) {
 		name_ = new graph_name(n);
 	}
 
-	graph(int n, std::vector<unsigned int> left, std::vector<unsigned int> right) : left_(left), right_(right) {
+	graph(int n, std::vector<unsigned int> left, std::vector<unsigned int> right) : left(left), right(right) {
 		name_ = new graph_name(n);
 	}
 
@@ -51,23 +52,39 @@ public:
 		// just copy the vectors 
 		graph_t* this_copy = new graph(0);
 		this_copy->name_ = name_->copy();
-		this_copy->left_ = left_;
-		this_copy->right_ = right_;
+		this_copy->left = left;
+		this_copy->right = right;
 
 		// save memory 
-		left_.shrink_to_fit();
-		right_.shrink_to_fit();
+		left.shrink_to_fit();
+		right.shrink_to_fit();
 	
 		return this_copy;
 	}
 
 	// getters 
-	std::vector<unsigned int> inline const &left() const { return left_; };
-	std::vector<unsigned int> inline const &right() const { return right_; };
 	graph_name_t inline const *name() const { return name_; };
 
 	// hasher 
 	size_t inline hash() const;
+
+	// add particules
+	void inline add_left(unsigned int n) {
+		left.push_back(n);
+		std::inplace_merge(left.begin(), left.end() - 1, left.end());
+	}
+	void inline add_left(std::vector<unsigned int> n) {
+		left.insert(left.end(), n.begin(), n.end());
+		std::inplace_merge(left.begin(), left.end() - n.size(), left.end());
+	}
+	void inline add_right(int n) {
+		right.push_back(n);
+		std::inplace_merge(right.begin(), right.end() - 1, right.end());
+	}
+	void inline add_right(std::vector<unsigned int> n) {
+		right.insert(right.end(), n.begin(), n.end());
+		std::inplace_merge(right.begin(), right.end() - n.size(), right.end());
+	}
 
 	// randomizer 
 	void randomize(unsigned int n);
[…]

### 2021-06-02 v4/classical/rules.hpp

@@ -6,55 +6,52 @@
 #include <vector>
 
 /* function to get all split and merges */
-std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
-	std::vector<graph::split_merge_t> split_merge;
+std::vector<graph::op_t> inline get_split_merge(graph_t const* graph) {
+	std::vector<graph::op_t> split_merge;
 
-	auto last_left = graph->left().end() - 1;
-	auto last_right = graph->right().end() - 1;
-	unsigned int last_idx = graph->size() - 1;
+	unsigned int const last_idx = graph->size() - 1;
 
-	auto left_it = graph->left().begin();
-	auto right_it = graph->right().begin();
+	auto left_it = graph->left.begin();
+	auto right_it = graph->right.begin();
 	bool first_or_last_split = *left_it == *right_it && *left_it == 0;
-	while (true) {
-		/* check if there are any particules left after iterating */
-		if (right_it > last_right ||
-		left_it > last_left)
-			break;
+	first_or_last_split |= graph->left.back() == last_idx && graph->right.back() == last_idx;
 
+	auto const left_end = graph->left.end();
+	auto const right_end = graph->right.end();
+	while (right_it < right_end && left_it < left_end)
 		if (*left_it == *right_it) {
-			/* check for split */
-			split_merge.push_back({(*left_it), graph->split_t});
-
-			/* check for last split */
-			if (*right_it == last_idx)
-				first_or_last_split = true;
+			// check for split
+			split_merge.push_back({*left_it, graph->split_t});
 
 			++right_it;
 			++left_it;
 		} else if (*left_it < *right_it) {
-			/* chedk for merges */
+			// chedk for merges
 			if (*left_it == *right_it - 1)
-				if (left_it == last_left) {
-					split_merge.push_back({(*left_it), graph->merge_t});
+				if (left_it == left_end - 1) {
+					split_merge.push_back({*left_it, graph->merge_t});
 				} else if (*(left_it + 1) != *right_it)
-					split_merge.push_back({(*left_it), graph->merge_t});
+					split_merge.push_back({*left_it, graph->merge_t});
 
 			++left_it;
 		} else
 			++right_it;
-	}
 		
 	if (!first_or_last_split)
-		if (*last_left == last_idx &&
-		graph->right()[0] == 0)
+		if (graph->left.back() == last_idx && graph->right[0] == 0)
[…]

### 2021-06-02 v4/quantum/rules.hpp

@@ -5,6 +5,7 @@
 #include <utility> //for pairs
 #include <complex> //for complex
 #include "../classical/graph.hpp"
+#include <tbb/concurrent_vector.h>
 
 bool inline check_zero(const std::complex<long double>& mag) {
 	const long double double_tolerance = 1e-30;
@@ -15,15 +16,15 @@ bool inline check_zero(const std::complex<long double>& mag) {
 
 /* count the number of subsets */
 template<class T>
-int num_subset(std::vector<T> const &vect) {
+int static num_subset(std::vector<T> const &vect) {
 	return pow(2, vect.size());
 }
 
 /* create a subset and a probability from the subset indice */
-std::pair<std::vector<graph::split_merge_t>, std::complex<long double>> subset(std::vector<graph::split_merge_t>& split_merge, int subset_numb,
+std::pair<std::vector<graph::op_t>, std::complex<long double>> static subset(std::vector<graph::op_t>& split_merge, int subset_numb,
 	std::complex<long double>& non_merge, std::complex<long double>& merge) {
 	
-	std::vector<graph::split_merge_t> res;
+	std::vector<graph::op_t> res;
 	std::complex<long double> proba = 1;
 
 	for (int i = 0; i < split_merge.size(); ++i) {
@@ -46,12 +47,63 @@ std::pair<std::vector<graph::split_merge_t>, std::complex<long double>> subset(s
 	return {res, proba};
 }
 
-std::pair<std::vector<graph::split_merge_t>, std::complex<long double>> subset(std::vector<graph::split_merge_t>& split_merge, int subset_numb,
-	long double teta, long double phi) {
+//to create a reversible dynamic
+std::pair<std::complex<long double>, std::complex<long double>> unitary(long double teta, long double phi) {
+	std::complex<long double> non_merge_ = std::cos(teta);
+	std::complex<long double> merge_ = std::polar(std::sin(teta), phi);
+	return {non_merge_, merge_};
+} 
 
-	/* compute amplitudes */
-	std::complex<long double> non_merge = std::cos(teta);
-	std::complex<long double> merge = std::polar(std::sin(teta), phi);
+// split merge a graph
+auto split_merge_all(std::complex<long double>& non_merge, std::complex<long double>& merge) {
+	return [&](graph_t* g) {
+		auto split_merge = get_split_merge(g);
[…]

### 2021-06-02 v4/quantum/state.hpp

@@ -2,12 +2,13 @@
 
 #include <vector>
 #include <utility>
+#include <functional>
 #include <complex> //for complex
 #include <string>
 #include "../classical/graph.hpp"
-#include "../classical/rules.hpp"
 #include "rules.hpp"
 #include <tbb/concurrent_unordered_map.h>
+#include <tbb/concurrent_vector.h>
 
 // forward definition of the state type
 typedef class state state_t;
@@ -35,10 +36,6 @@ private:
 	// main list 
 	graph_map_t graphs_;
 
-	// parameters
-	std::complex<long double> non_merge_ = -1;
-	std::complex<long double> merge_ = 0;
-
 	// checker
 	friend bool check(state_t* s);
 
@@ -55,21 +52,10 @@ public:
 	//reader
 	std::pair<long double, long double> size_stat();
 
-	// setter 
-	void set_params(long double teta, long double phi) {
-		// compute amplitude 
-		non_merge_ = std::cos(teta);
-		merge_ = std::polar(std::sin(teta), phi);
-	}
-
 	void reduce_all();
 
 	// dynamic 
-	void step_split_merge_all(bool step, bool split_merge, bool reversed);
-	void inline step_split_merge_all() { step_split_merge_all(true, true, false); }
-	void inline step_all() { step_split_merge_all(true, false, false); }
-	void inline split_merge_all() { step_split_merge_all(false, true, false); }
-	void inline reversed_split_merge_step() { step_split_merge_all(false, true, true); }
+	void step_all(std::function<tbb::concurrent_vector<std::pair<graph_t*, std::complex<long double>>>(graph_t* g)> rule);
 
 	// for debugging 
 	void print();
@@ -117,7 +103,7 @@ std::pair<long double, long double> state::size_stat() {
 }
 
 // dynamic 
-void state::step_split_merge_all(bool step, bool split_merge, bool reversed) {
+void state::step_all(std::function<tbb::concurrent_vector<std::pair<graph_t*, std::complex<long double>>>(graph_t* g)> rule) {
 	graph_map_t buff;
 	buff.swap(graphs_);
 
@@ -126,47 +112,12 @@ void state::step_split_merge_all(bool step, bool split_merge, bool reversed) {
   	for (auto & [graph, mag] : buff)
 	#pragma omp task
   	{
-  		if (step)
-  			graph->step();
-
-  		if (split_merge) {
[…]

### 2021-06-02 v4/tests/classical_iteration.cpp

@@ -18,8 +18,7 @@ int main() {
     graph_t* g_0 = g->copy();
 
     for (int i = n_iteration - 1; i >= 0; --i) {
-      auto split_merge = get_split_merge(g);
-      g->split_merge(split_merge);
+      split_merge(g);
       g->reversed_step();
       sizes[i] += g->size() / n_iter;
     }
@@ -28,8 +27,7 @@ int main() {
 
     for (int i = n_iteration + 1; i < 2*n_iteration + 1; ++i) {
       g_0->step();
-      auto split_merge = get_split_merge(g_0);
-      g_0->split_merge(split_merge);
+      split_merge(g_0);
       sizes[i] += g_0->size() / n_iter;
     }
   }

### 2021-06-02 v4/tests/quantum_injectivity_test.cpp

@@ -66,12 +66,14 @@ random:
 loop:
 
 		state_t* s = new state(g_1);
-		s->set_params(M_PI_4, M_PI_4);
+	    auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
+	    auto rule = step_split_merge_all(non_merge, merge);
+	    auto reversed_rule = reversed_step_split_merge_all(non_merge, merge);
 
 		int n_iter = 5;
 
 		for (int i = 0; i < n_iter; ++i) {
-			s->step_split_merge_all();
+			s->step_all(rule);
 			s->reduce_all();
 
 			#ifdef TEST
@@ -90,7 +92,7 @@ loop:
 		}
 
 		for (int i = 0; i < n_iter; ++i) {
-			s->reversed_split_merge_step();
+			s->step_all(reversed_rule);
 			s->reduce_all();
 
 			#ifdef TEST

### 2021-06-02 v4/tests/quantum_iteration.cpp

@@ -16,7 +16,8 @@ int main() {
     g_1->randomize(3);
 
     state_t* s = new state(g_1);
-	s->set_params(M_PI_4, M_PI_2);
+    auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
+    auto rule = step_split_merge_all(non_merge, merge);
 
     for (int i = 1; i < 11; ++i) {
 
@@ -30,7 +31,7 @@ int main() {
             printf("...OK\n");
         #endif
 
-        printf("\nstep_split_merge_all() ...\n"); s->step_split_merge_all();
+        printf("\nstep_split_merge_all() ...\n"); s->step_all(rule);
 
         //if (i % 3 == 0) {
             printf("reduce_all() ...\n\n"); s->reduce_all(); printf("\n");

### 2021-06-02 v4/classical/graph.hpp
added a 'create_erase' rule

@@ -30,8 +30,8 @@ private:
 	void rotate_once_right(std::vector<unsigned int>& pos);
 
 public:
-	std::vector<unsigned int> left;
-	std::vector<unsigned int> right;
+	std::vector<unsigned int> mutable left;
+	std::vector<unsigned int> mutable right;
 
 	// normal constructors 
 	graph(int n) {
@@ -68,24 +68,6 @@ public:
 	// hasher 
 	size_t inline hash() const;
 
-	// add particules
-	void inline add_left(unsigned int n) {
-		left.push_back(n);
-		std::inplace_merge(left.begin(), left.end() - 1, left.end());
-	}
-	void inline add_left(std::vector<unsigned int> n) {
-		left.insert(left.end(), n.begin(), n.end());
-		std::inplace_merge(left.begin(), left.end() - n.size(), left.end());
-	}
-	void inline add_right(int n) {
-		right.push_back(n);
-		std::inplace_merge(right.begin(), right.end() - 1, right.end());
-	}
-	void inline add_right(std::vector<unsigned int> n) {
-		right.insert(right.end(), n.begin(), n.end());
-		std::inplace_merge(right.begin(), right.end() - n.size(), right.end());
-	}
-
 	// randomizer 
 	void randomize(unsigned int n);
 	void randomize();
@@ -101,11 +83,14 @@ public:
   typedef enum op_type {
 		split_t,
 		merge_t,
+		erase_t,
+		create_t,
 	} op_type_t;
 	// typedef of the pair of an index and a op_type 
   	typedef std::pair<unsigned int, op_type_t> op_t;
   	// functions 
   	void inline split_merge(std::vector<op_t>& split_merge); //indexes have to be sorted !!
+  	void inline erase_create(std::vector<op_t>& erase_create); //indexes have to be sorted !!
 
   	// step function 
   	void inline step() {
@@ -126,6 +111,10 @@ public:
 size_t graph::hash() const {
 	if (hashed_)
 		return hash_;
+
+	// save memory 
+	left.shrink_to_fit();
+	right.shrink_to_fit();
 
 	hash_ = 0;
 	boost::hash<unsigned int> hasher;
@@ -195,7 +184,7 @@ void graph::rotate_once_right(std::vector<unsigned int>& pos) {
 
 // split merge 
 void graph::split_merge(std::vector<op_t>& split_merge) {
-	if (split_merge.empty())
[…]

### 2021-06-02 v4/classical/graph_name.hpp

@@ -3,6 +3,7 @@
 #include "node.hpp"
 #include <vector>
 #include <stdio.h>
+#include <algorithm>
 #include <boost/functional/hash.hpp>
 
 // forward declaration of the graph_t type 

### 2021-06-02 v4/classical/rules.hpp

@@ -5,9 +5,12 @@
 #include <utility> //for pairs
 #include <vector>
 
-/* function to get all split and merges */
+// function to get all split and merges 
 std::vector<graph::op_t> inline get_split_merge(graph_t const* graph) {
 	std::vector<graph::op_t> split_merge;
+	
+	if (graph->right.empty() || graph->left.empty())
+		return split_merge;
 
 	unsigned int const last_idx = graph->size() - 1;
 
@@ -50,6 +53,69 @@ void split_merge(graph_t* graph) {
 	graph->split_merge(split_merges);
 }
 
+//function to get all void and split
+std::vector<graph::op_t> inline get_erase_create(graph_t const* graph) {
+	std::vector<graph::op_t> create_erase;
+
+	unsigned int const last_idx = graph->size() - 1;
+
+	auto left_it = graph->left.begin();
+	auto right_it = graph->right.begin();
+
+	unsigned int last_pos = 0;
+
+	auto const left_end = graph->left.end();
+	auto const right_end = graph->right.end();
+	while (right_it < right_end && left_it < left_end) {
+		// add create
+		unsigned int next_last_pos = std::min(*left_it, *right_it);
+		for (unsigned int i = last_pos; i < next_last_pos; ++i)
+			create_erase.push_back({i, graph->create_t});
+
+		// update lest_pos
+		last_pos = next_last_pos + 1;
+
+		if (*left_it == *right_it) {
+			// check for erase
+			create_erase.push_back({*left_it, graph->erase_t});
+
+			++right_it;
+			++left_it;
+		} else {
+			if (*left_it < *right_it) {
+				++left_it;
+			} else
+				++right_it;
+		}
+	}
+		
+	// complete the unfinished list
+	auto it = left_it == left_end ? right_it : left_it;
+	auto const end = left_it == left_end ? right_end : left_end;
+	for (;it < end; ++it) {
+		// add create
+		unsigned int next_last_pos = *it;
+		for (unsigned int i = last_pos; i < next_last_pos; ++i)
+			create_erase.push_back({i, graph->create_t});
+
+		// update lest_pos
+		last_pos = next_last_pos + 1;
+	}
+	
+	// add create at the end
+	unsigned int const size = graph->size();
+	for (unsigned int i = last_pos; i < size; ++i)
+		create_erase.push_back({i, graph->create_t});
+
+	return create_erase;
+}
+
+// erase create a graph
[…]

### 2021-06-02 v4/quantum/rules.hpp

@@ -5,6 +5,7 @@
 #include <utility> //for pairs
 #include <complex> //for complex
 #include "../classical/graph.hpp"
+#include "../classical/rules.hpp"
 #include <tbb/concurrent_vector.h>
 
 bool inline check_zero(const std::complex<long double>& mag) {
@@ -28,7 +29,7 @@ std::pair<std::vector<graph::op_t>, std::complex<long double>> static subset(std
 	std::complex<long double> proba = 1;
 
 	for (int i = 0; i < split_merge.size(); ++i) {
-		long double sign = 1 - 2*split_merge[i].second;
+		long double sign = 1 - 2*(split_merge[i].second % 2);
 
 		/* i_th bit of subset_numb */
 		if (subset_numb%2) {
@@ -86,6 +87,39 @@ auto split_merge_all(std::complex<long double>& non_merge, std::complex<long dou
 	};
 }
 
+// split merge a graph
+auto erase_create_all(std::complex<long double>& non_create, std::complex<long double>& create) {
+	return [&](graph_t* g) {
+		auto erase_create = get_erase_create(g);
+		tbb::concurrent_vector<std::pair<graph_t*, std::complex<long double>>> graphs;
+
+		#pragma omp parallel
+		{
+			#pragma omp task
+		  	{
+		  		// update the probability of the graph without split or merge 
+				auto [_, mag_no_erase_create] = subset(erase_create, 0, non_create, create);
+				graphs.push_back({g, mag_no_erase_create});
+		  	}
+
+			// add all graphs that actually have some split ot merge 
+			const int n_max = num_subset(erase_create);
+			for (int j = 1; j < n_max; ++j)
+			#pragma omp task
+			{
+				graph_t* g_ = g->copy();
+
+				auto [split_merge_list, mag_erase_create] = subset(erase_create, j, non_create, create);
+				g_->erase_create(split_merge_list);
+				graphs.push_back({g_, mag_erase_create});
+			}
+		}
+
+		return graphs;
+	};
+}
+
+//step and split merge
 auto step_split_merge_all(std::complex<long double>& non_merge, std::complex<long double>& merge) {
 	return [&](graph_t* g) {
 		auto const split_merge_all_ = split_merge_all(non_merge, merge);
@@ -98,6 +132,29 @@ auto reversed_step_split_merge_all(std::complex<long double>& non_merge, std::co
 	return [&](graph_t* g) {
[…]

### 2021-06-02 v4/tests/classical_injectivity_test.cpp

@@ -17,17 +17,16 @@ int main() {
       graph_t* c = g->copy();
 
       g->step();
-      auto split_merge = get_split_merge(g);
-      g->split_merge(split_merge);
+      g->reversed_step();
+      split_merge(g);
 
       graph_t* c2 = g->copy();
 
-      split_merge = get_split_merge(c2);
-      c2->split_merge(split_merge);
-      c2->reversed_step();
+      split_merge(c2);
+      erase_create(c2);
+      erase_create(c2);
 
-
-      if (c2->hash() != c->hash() /*!g->equal(c)*/){
+      if (c->hash() != c2->hash() /*!g->equal(c)*/){
         c2->print(); printf("\n");
         c->print(); printf("\n");
         throw;

### 2021-06-02 v4/tests/graph_test.cpp

@@ -58,19 +58,67 @@ random:
 loop:
     graph_t* g_2 = g_1->copy();
 
+    //--------------
+
+    g_1->step();
+    printf("\n\nstep():           "); g_1->print();
+
+    //---
+
+    g_1->reversed_step();
+    printf("\nreversed_step():  "); g_1->print();
+
+    //--------------
+
     auto split_merge = get_split_merge(g_1);
-    printf("\n"); print_split_merge(split_merge); printf("\n");
+    printf("\n\n"); print_split_merge(split_merge);
 
     g_1->split_merge(split_merge);
     printf("\nmerge_split():    "); g_1->print();
+
+    //---
 
     split_merge = get_split_merge(g_1);
+    printf("\n"); print_split_merge(split_merge);
 
-    printf("\n"); print_split_merge(split_merge); printf("\n");
     g_1->split_merge(split_merge);
     printf("\nmerge_split():    "); g_1->print();
 
-    printf("\ncopy*:            "); g_2->print();
+    //--------------
+
+    auto erase_create = get_erase_create(g_1);
+    printf("\n\n"); print_erase_create(erase_create);
+    
+    g_1->erase_create(erase_create);
+    printf("\nerase_create():   "); g_1->print();
+
+    printf("\n\nleft: ");
+    for (auto &l : g_1->left)
+      printf("%d, ", l);
+    printf("\nright: ");
+    for (auto &l : g_1->right)
+      printf("%d, ", l);
+    printf("\n");
+
+    //---
+
+    erase_create = get_erase_create(g_1);
+    printf("\n"); print_erase_create(erase_create);
+    
+    g_1->erase_create(erase_create);
+    printf("\nerase_create():   "); g_1->print();
+
+    printf("\n\nleft: ");
+    for (auto &l : g_1->left)
+      printf("%d, ", l);
+    printf("\nright: ");
+    for (auto &l : g_1->right)
+      printf("%d, ", l);
+    printf("\n");
+
+    //--------------
+
+    printf("\n\ncopy*:            "); g_2->print();
 
     printf("\nhashes are: %ld %ld\n", g_1->hash(), g_2->hash());
 

### 2021-06-02 v4/tests/quantum_injectivity_test.cpp

@@ -67,6 +67,7 @@ loop:
 
 		state_t* s = new state(g_1);
 	    auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
+
 	    auto rule = step_split_merge_all(non_merge, merge);
 	    auto reversed_rule = reversed_step_split_merge_all(non_merge, merge);
 
@@ -83,13 +84,11 @@ loop:
 					printf("\nstate is not OK\n");
 			#endif
 		}
+
+		//----
 		
-		if (n_iter <= 2) {
-			printf("\nafter %d step_merge_split():\n", n_iter); s->print();
-		} else {
-			auto [avg, std_dev] = s->size_stat();
-        	printf("%ld graph of size %Lf±%Lf after %d step_merge_split()\n", s->graphs().size(), avg, std_dev, n_iter);
-		}
+		auto [avg, std_dev] = s->size_stat();
+        printf("%ld graph of size %Lf±%Lf after %d step_merge_split()\n", s->graphs().size(), avg, std_dev, n_iter);
 
 		for (int i = 0; i < n_iter; ++i) {
 			s->step_all(reversed_rule);
@@ -103,6 +102,42 @@ loop:
 			#endif
 		}
 
-		printf("\nafter %d reversed_merge_split_step():\n", n_iter); s->print();
+		printf("\nafter %d reversed_step_merge_split():\n", n_iter); s->print();
+
+		//--------------------------
+
+		auto rule_ = step_erase_create_all(non_merge, merge);
+	    auto reversed_rule_ = reversed_step_erase_create_all(non_merge, merge);
+
+		for (int i = 0; i < n_iter; ++i) {
+			s->step_all(rule_);
+			s->reduce_all();
+
+			#ifdef TEST
+				if (check(s)) {
+					printf("\nstate is OK\n");
+				} else
+					printf("\nstate is not OK\n");
+			#endif
+		}
+
+		//----
+		
+		auto [avg_, std_dev_] = s->size_stat();
+        printf("%ld graph of size %Lf±%Lf after %d step_erase_create_all()\n", s->graphs().size(), avg_, std_dev_, n_iter);
+
+		for (int i = 0; i < n_iter; ++i) {
+			s->step_all(reversed_rule_);
+			s->reduce_all();
+
+			#ifdef TEST
+				if (check(s)) {
+					printf("\nstate is OK\n");
+				} else
+					printf("\nstate is not OK\n");
+			#endif
+		}
+
[…]

### 2021-06-03 v5/paper/paper.tex
created a new version

--- 2021-06-02 paper/paper.tex
@@
 class graph {
+	// split_merge type enum 
+  	typedef enum op_type {
+		split_t,
+		merge_t,
+		erase_t,
+		create_t,
+	} op_type_t;
+
+	// typedef of the pair of an index and a op_type 
+  	typedef std::pair<unsigned int, op_type_t> op_t;
+
 	// variables 
@@
 		}
+	}
+	//...
+\end{lstlisting}
+
+\subsubsection{erase\_create()}
+
+\begin{lstlisting}[style=CStyle]
+
+void inline graph::erase_create(std::vector<op_t>& erase_create) {
+	//...
+	void inline erase_create(std::vector<op_t>& erase_create) {
+		auto const erase_create_begin = erase_create.rend();
+
+		// add and remove left particules
+		auto erase_create_it = erase_create.rbegin();
+		int left_idx = left.size() - 1;
+		if (!left.empty())
+			for (; erase_create_it < erase_create_begin; ++erase_create_it)
+				if (erase_create_it->second == create_t) {
+					// find the position to insert
+					for (; left[left_idx] >= erase_create_it->first && left_idx >= 0; --left_idx) {}
+
+					if (left_idx < 0)
+						break;
+
+					// insert
+					left.insert(left.begin() + left_idx + 1, erase_create_it->first);
+
+				} else {
+					// find the particule to erase 
+					for (; left[left_idx] > erase_create_it->first && left_idx >= 0; --left_idx) {}
+
+					if (left_idx < 0)
+						break;
+
+					// erase
+					left.erase(left.begin() + left_idx);
+					--left_idx;
+				}
+
+		// add the particule at the begin
+		for (; erase_create_it < erase_create_begin; ++erase_create_it)
+			left.insert(left.begin(), erase_create_it->first);
+
+		/* add and remove right particules */
 	}

### 2021-06-03 v5/classical/checks.hpp

@@ -1,0 +1,8 @@
+#pragma once
+
+#include "graph.hpp"
+
+/* to check */
+bool inline graph_checker(graph_t* graph) {
+	return true;
+}

### 2021-06-03 v5/classical/graph.hpp

@@ -1,0 +1,230 @@
+#pragma once
+
+#include "graph_name.hpp"
+#include <cstdlib>
+#include <ctime>
+#include <ranges>
+
+// forward declaration of the graph_t type 
+typedef class graph graph_t;
+size_t const separator = -1; 
+
+class graph {
+public:
+  	// split_merge type enum 
+  	typedef enum op_type {
+		split_t,
+		merge_t,
+		erase_t,
+		create_t,
+	} op_type_t;
+
+	// typedef of the pair of an index and a op_type 
+  	typedef std::pair<unsigned short int, op_type_t> op_t;
+
+  	// particules positions
+  	std::vector<bool> mutable left;
+	std::vector<bool> mutable right;
+
+private:
+	// variables 
+	graph_name_t* name_;
+
+	// hash
+	size_t mutable hash_ = 0;
+	bool mutable hashed_ = false;
+
+public:
+	// normal constructors 
+	graph(short int n) {
+		left = std::vector<bool>(n, false);
+		right = std::vector<bool>(n, false);
+		name_ = new graph_name(n);
+	}
+
+	graph(std::vector<bool> left, std::vector<bool> right) : left(left), right(right) {
+		if (left.size() != right.size())
+			throw;
+
+		name_ = new graph_name(left.size());
+	}
+
+	// size operator 
+	size_t inline size() const {
+		return name_->size();
+	};
+
+	// copy opperator 
+	graph_t inline *copy() {
+		// just copy the vectors 
+		graph_t* this_copy = new graph(0);
+		this_copy->name_ = name_->copy();
+		this_copy->left = left;
+		this_copy->right = right;
+
+		// save memory 
+		left.shrink_to_fit();
+		right.shrink_to_fit();
+	
+		return this_copy;
+	}
+
+	// getters 
+	graph_name_t inline const *name() const { return name_; };
+
+	// hasher 
+	size_t inline hash() const;
+
+	// randomizer 
+	void randomize();
+
+	// comparators 
+  	//bool inline equal(graph_t* other) const;
+
+	// split and merge 
+  	void inline split_merge(std::vector<op_t>& split_merge); //indexes have to be sorted !!
+  	void inline erase_create(std::vector<op_t>& erase_create); //indexes have to be sorted !!
+
+  	// step function 
+  	void inline step();
+  	void inline reversed_step() {
+  		std::swap(left, right);
+  		step();
[…]

### 2021-06-03 v5/classical/graph_name.hpp

@@ -1,0 +1,173 @@
+#pragma once
+
+#include "node.hpp"
+#include <algorithm>
+
+// forward declaration of the graph_t type 
+typedef class graph_name graph_name_t;
+
+class graph_name {
+private:
+	// node list 
+	std::vector<node_t> mutable nodes_;
+	std::vector<node_t> mutable node_buff_;
+	std::vector<short int> mutable trash_collection_;
+
+	// hash
+	size_t mutable hash_ = 0;
+	bool mutable hashed_ = false;
+
+	short int push_to_buffer(node_t &n) {
+		if (trash_collection_.empty()) {
+			node_buff_.push_back(n);
+			return node_buff_.size() - 1;
+		}
+
+		short int buff_idx = trash_collection_.back();
+		trash_collection_.pop_back();
+		node_buff_[buff_idx] = n;
+		return buff_idx;
+	}
+
+	// debugging
+	friend void print(graph_name_t const *name, short int n);
+
+public:
+	// normal constructors 
+	graph_name(unsigned short int size) {
+		for (short int i = 0; i < size; ++i)
+			nodes_.emplace_back(i);
+	}
+
+	// getters
+	std::vector<node_t> const &nodes() const { return nodes_; }
+
+	// size operator 
+	size_t inline size() const {
+		return nodes_.size();
+	}
+
+	// copy opperator 
+	graph_name_t inline *copy() {
+		// just copy the vector 
+		graph_name_t* this_copy = new graph_name(0);
+		this_copy->nodes_ = nodes_;
+		this_copy->node_buff_ = node_buff_;
+		this_copy->trash_collection_ = trash_collection_;
+
+		return this_copy;
+	}
+
+	//hasher
+	size_t inline hash() const {
+		if (hashed_)
+			return hash_;
+
+		// memory managment at hashing time
+		trash_collection_.shrink_to_fit();
+		node_buff_.shrink_to_fit();
+		nodes_.shrink_to_fit();
+
+		hash_ = 0;
+
+		/* combine all nodes hash */
+		for (auto &n : nodes_)
+			boost::hash_combine(hash_, n.hash());
+
+		hashed_ = true;
+		return hash_;
+	}
+
+	// split and merge 
+  	bool inline split(unsigned short int idx);
+  	void inline merge(unsigned short int idx);
+};
+
+// split merge
+bool inline graph_name::split(unsigned short int idx) {
+	hashed_ = false;
+
+	node_t node = nodes_[idx];
+	if (node.is_pair()) {
+		// read indexes
[…]

### 2021-06-03 v5/classical/node.hpp

@@ -1,0 +1,137 @@
+#pragma once
+
+#include <stdio.h>
+#include <vector>
+#include <boost/functional/hash.hpp>
+
+// forward declaration of the node_t type 
+typedef struct node node_t;
+
+short int const point_l_idx = -1;
+short int const point_r_idx = -2;
+short int const element_idx = -3;
+
+struct node {
+private:
+	short int left_idx__or_element_;
+	short int right_idx__or_type_;
+	size_t hash_ = 0;
+	bool has_most_left_zero_ = false;
+public:
+
+	// constructors
+	node(short int n) :
+		left_idx__or_element_(n), right_idx__or_type_(element_idx) {
+
+		hash_ = n;
+		boost::hash_combine(hash_, element_idx);
+		
+		has_most_left_zero_ = n == 0;
+	}
+
+	node(short int const idx, node_t const &other, short int const type) :
+		left_idx__or_element_(idx), right_idx__or_type_(type) {
+
+		boost::hash_combine(hash_, other.hash_);
+		boost::hash_combine(hash_, type);
+
+		// check for most left zero
+		if (is_left())
+			has_most_left_zero_ = other.has_most_left_zero_;
+	}
+
+	node(short int const left_idx, node_t const &left, short int const right_idx, node_t const &right) :
+		left_idx__or_element_(left_idx), right_idx__or_type_(right_idx){
+
+		boost::hash_combine(hash_, left.hash_);
+		boost::hash_combine(hash_, right.hash_);
+		has_most_left_zero_ = left.has_most_left_zero_ || right.has_most_left_zero_;
+	}
+
+	// getters
+	size_t inline hash() const { return hash_; }
+	short int inline left_idx() const { return left_idx__or_element_; }
+	short int inline right_idx() const { return right_idx__or_type_; }
+	bool inline has_most_left_zero() const { return has_most_left_zero_; }
+
+	// type getters
+	bool inline is_element() const { return right_idx__or_type_ == element_idx; }
+	bool inline is_pair() const { return right_idx__or_type_ >= 0; }
+	bool inline is_left() const { return right_idx__or_type_ == point_l_idx; };
+	bool inline is_right() const { return right_idx__or_type_ == point_r_idx; };
+};
+
+//---------------------------------------------------------
+// non member functions
+//---------------------------------------------------------
+
+// debuging 
[…]

### 2021-06-03 v5/classical/rules.hpp

@@ -1,0 +1,77 @@
+#pragma once
+
+#include "graph.hpp"
+
+// function to get all split and merges 
+std::vector<graph::op_t> inline get_split_merge(graph_t const* graph) {
+	std::vector<graph::op_t> split_merges;
+	
+	auto const size_ = graph->size();
+	for (int i = 0; i < size_; ++i)
+		if (graph->left[i] && graph->right[i]) {
+			split_merges.push_back({i, graph->split_t});
+		} else {
+			// next pos
+			unsigned short int next_pos = (i + 1) % size_; 
+
+			if (graph->left[i] && graph->right[next_pos] && !graph->left[next_pos])
+				split_merges.push_back({i, graph->merge_t});
+		}
+
+	return split_merges;
+}
+
+// split merge a graph
+void split_merge(graph_t* graph) {
+	auto split_merges = get_split_merge(graph);
+	graph->split_merge(split_merges);
+}
+
+//function to get all void and split
+std::vector<graph::op_t> inline get_erase_create(graph_t const* graph) {
+	std::vector<graph::op_t> create_erases;
+
+	for (int i = 0; i < graph->size(); ++i)
+		if (graph->left[i] && graph->right[i]) {
+			create_erases.push_back({i, graph->erase_t});
+		} else if (!graph->left[i] && !graph->right[i])
+			create_erases.push_back({i, graph->create_t});
+
+	return create_erases;
+}
+
+// erase create a graph
+void erase_create(graph_t* graph) {
+	auto erase_creates = get_erase_create(graph);
+	graph->erase_create(erase_creates);
+}
+
+/* for debugging */
+void print_split_merge(std::vector<graph::op_t>& split_merge) {
+	graph_t* graph;
+
+	printf("merge at indexes ");
+	for (auto & it : split_merge)
+		if (it.second == graph->merge_t)
+			printf("%u, ", it.first);
+
+	printf("\nsplit at indexes ");
+	for (auto & it : split_merge)
+		if (it.second == graph->split_t)
+			printf("%u, ", it.first);
+}
+
+/* for debugging */
+void print_erase_create(std::vector<graph::op_t>& create_erase) {
+	graph_t* graph;
+
+	printf("create at indexes ");
+	for (auto & it : create_erase)
+		if (it.second == graph->create_t)
+			printf("%u, ", it.first);
+
+	printf("\nerase at indexes ");
+	for (auto & it : create_erase)
+		if (it.second == graph->erase_t)
+			printf("%u, ", it.first);
+}

### 2021-06-03 v5/grapher/1d_graph.py

@@ -1,0 +1,10 @@
+from matplotlib import pyplot as plt
+import sys
+import numpy as np
+
+with open("res.txt", 'r') as file:
+    nums = file.read()
+    plots = list(map(float, nums.split(',')))
+    plt.plot(np.arange(-len(plots) // 2, len(plots) // 2), plots, linewidth=1)
+
+plt.savefig('graph.png')

### 2021-06-03 v5/grapher/classical_iteration.cpp

@@ -1,0 +1,35 @@
+#include "../classical/rules.hpp"
+#include "../classical/graph.hpp"
+#include "../classical/checks.hpp"
+
+const int n_iteration = 1000;
+const int n_iter = 20;
+
+int main() {
+  std::vector<float> sizes(2*n_iteration + 1, 0);
+
+  for (int j = 0; j < n_iter - 1; ++j) {
+    graph_t* g = new graph(50);
+    g->randomize(4);
+
+    graph_t* g_0 = g->copy();
+
+    for (int i = n_iteration - 1; i >= 0; --i) {
+      split_merge(g);
+      g->reversed_step();
+      sizes[i] += g->size() / n_iter;
+    }
+
+    sizes[n_iteration] += g_0->size() / n_iter;
+
+    for (int i = n_iteration + 1; i < 2*n_iteration + 1; ++i) {
+      g_0->step();
+      split_merge(g_0);
+      sizes[i] += g_0->size() / n_iter;
+    }
+  }
+
+  printf("%f", sizes[0]);
+    for (auto &s : sizes)
+      printf(",%f", s);
+}

### 2021-06-03 v5/grapher/quantum_iteration.cpp

@@ -8,16 +8,16 @@
 #include <cmath>
 
 #define RULE "split_merge_step_erase_create_all"; //"step_split_merge_all" //"step_erase_create_all"
-#define SIZE 4
+#define SIZE 5
 #define N_ITER 3
 
 int main() {
     auto rule_ = RULE;
 
-    graph_t* g_1 = new graph(5, {0, 3},  {0, 2, 4});
-
+    graph_t* g_1 = new graph({true, false, false, true, false},  {true, false, true, false, true});
+    
     /*graph_t* g_1 = new graph(SIZE);
-    g_1->randomize(2);*/
+    g_1->randomize();*/
 
     state_t* s = new state(g_1);
     auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);

### 2021-06-03 v5/quantum/checks.hpp

@@ -1,0 +1,43 @@
+#pragma once
+
+#include "state.hpp"
+#include "rules.hpp"
+#include "../classical/checks.hpp"
+
+const double probability_tolerance = 1e-5;
+
+bool check(state_t* s) {
+	auto data = s->graphs();
+	auto end = data.end();
+	double probability = 0;
+
+	//iterate over all graphs
+    for(auto it = data.begin(); it != data.end(); ++it) {
+    	//add probability
+    	probability += std::norm(it->second);
+
+    	//check if a probability is under zero
+		if (check_zero(it->second)) {
+			printf("probability is zero!!\n");
+			return false;
+		}
+
+		//check graph
+		if (!graph_checker(it->first))
+			return false;
+
+    	//iterate over all graphs
+    	if (data.count(it->first) != 1) {
+			printf("two graphs with the same hash!!\n");
+			return false;
+		}
+    }
+
+	//check for probability
+	if (probability > 1 + probability_tolerance || probability < 1 - probability_tolerance) {
+		printf("probability not equal 1 (%f)!!\n", probability);
+		return false;
+	}
+
+	return true;
+}

### 2021-06-03 v5/quantum/rules.hpp

@@ -1,0 +1,167 @@
+#pragma once
+
+#include <math.h>  //pow
+#include <complex> //for complex
+#include "../classical/graph.hpp"
+#include "../classical/rules.hpp"
+#include <tbb/concurrent_vector.h>
+
+/* count the number of subsets */
+template<class T>
+int static num_subset(std::vector<T> const &vect) {
+	return std::pow(2, vect.size());
+}
+
+/* create a subset and a probability from the subset indice */
+std::pair<std::vector<graph::op_t>, std::complex<double>> static subset(std::vector<graph::op_t>& split_merge, int subset_numb,
+	std::complex<double>& non_merge, std::complex<double>& merge) {
+	
+	std::vector<graph::op_t> res;
+	std::complex<double> proba = 1;
+
+	for (int i = 0; i < split_merge.size(); ++i) {
+		double sign = 1 - 2*(split_merge[i].second % 2);
+
+		/* i_th bit of subset_numb */
+		if (subset_numb%2) {
+			/* add opperation to res */
+			res.push_back(split_merge[i]);
+
+			/* get proba */
+			proba *= std::complex<double>(merge.real(), sign*merge.imag());
+		} else
+			proba *= sign*non_merge;
+
+
+		subset_numb /= 2;
+	}
+
+	return {res, proba};
+}
+
+//to create a reversible dynamic
+std::pair<std::complex<double>, std::complex<double>> unitary(double teta, double phi) {
+	std::complex<double> non_merge_ = std::cos(teta);
+	std::complex<double> merge_ = std::polar(std::sin(teta), phi);
+	return {non_merge_, merge_};
+} 
+
+// split merge a graph
+auto split_merge_all(std::complex<double>& non_merge, std::complex<double>& merge) {
+	return [&](graph_t* g) {
+		auto split_merge = get_split_merge(g);
+		tbb::concurrent_vector<std::pair<graph_t*, std::complex<double>>> graphs;
+
+		#pragma omp parallel
+		{
+			#pragma omp task
+		  	{
+		  		// update the probability of the graph without split or merge 
+				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge, merge);
+				graphs.push_back({g, mag_no_split_merge});
+		  	}
+
+			// add all graphs that actually have some split ot merge 
+			const int n_max = num_subset(split_merge);
+			for (int j = 1; j < n_max; ++j)
+			#pragma omp task
+			{
[…]

### 2021-06-03 v5/quantum/state.hpp

@@ -1,0 +1,189 @@
+#pragma once
+
+#include <complex> //for complex
+#include "../classical/graph.hpp"
+#include <tbb/concurrent_unordered_map.h>
+#include <tbb/concurrent_vector.h>
+#include <map>
+
+// check zero probability
+bool inline check_zero(const std::complex<double>& mag) {
+	const double double_tolerance = 1e-30;
+	return std::norm(mag) <= double_tolerance;
+	/*const std::complex<double> zero = 0;
+	return mag == zero;*/
+}
+
+// forward definition of the state type
+typedef class state state_t;
+
+class state {
+public:
+	// hasher
+	struct graph_hasher {
+		size_t operator()(graph_t* const &g) const {
+			return g->hash();
+		}
+	};
+
+	// comparator
+	struct graph_comparator {
+		bool operator()(graph_t* const &g1, graph_t* const &g2) const {
+			return g1->hash() == g2->hash();
+		}
+	};
+
+	// type definition
+	typedef tbb::concurrent_unordered_multimap<graph_t*, std::complex<double>, graph_hasher, graph_comparator> graph_map_t;
+
+private:
+	// main list 
+	graph_map_t graphs_;
+
+public:
+	// single graph constructor 
+	state(graph_t* g) {
+		// add graph 
+		graphs_.insert({g, {1, 0}});
+	}
+
+	//getter
+	auto const &graphs() { return graphs_; }
+
+	// reduce
+	void reduce_all();
+
+	// dynamic 
+	void step_all(std::function<tbb::concurrent_vector<std::pair<graph_t*, std::complex<double>>>(graph_t* g)> rule);
+};
+
+// insert operators 
+void state::reduce_all() {
+	#ifdef VERBOSE
+		printf("reducing %ld graphs...\n", graphs_.size());
+	#endif
+
+    for(auto it = graphs_.begin(); it != graphs_.end();) {
+    	// range of similar graphs to delete
+    	auto upper = graphs_.equal_range(it->first).second;
+
+    	for(auto jt = std::next(it); jt != upper; ++jt)
+        	it->second += jt->second;
+
+    	// if the first graphgs has a zero probability, erase the whole range
+    	if (!check_zero(it->second))
+    		++it;
+    	
+    	it = graphs_.unsafe_erase(it, upper);
+    }
+}
+
+// dynamic 
[…]

### 2021-06-03 v5/tests/classical_injectivity_test.cpp

@@ -1,0 +1,40 @@
+#include "../classical/rules.hpp"
+#include "../classical/graph.hpp"
+#include "../classical/checks.hpp"
+
+int main() {
+  #pragma omp parallel
+  #pragma omp single
+  for (int j = 0; j < 1000; ++j)
+  #pragma omp task
+  {
+    
+    graph_t* g = new graph(10);
+
+    for (int i = 0; i < 20; ++i) {
+      g->randomize();
+      graph_t* c = g->copy();
+
+      g->step();
+      g->reversed_step();
+      split_merge(g);
+
+      graph_t* c2 = g->copy();
+
+      split_merge(c2);
+      erase_create(c2);
+      erase_create(c2);
+
+      if (c->hash() != c2->hash() /*!g->equal(c)*/){
+        print(c2); printf("\n");
+        print(c); printf("\n");
+        throw;
+      }
+
+      if (!graph_checker(g))
+        throw;
+    }
+  }
+    
+  printf("Ok\n");
+}

### 2021-06-03 v5/tests/graph_name_test.cpp

@@ -1,0 +1,30 @@
+#include "../classical/graph_name.hpp"
+
+int main() {
+  graph_name_t* n_1 = new graph_name(6);
+  printf("*new graph_name(6): "); print(n_1);
+
+  graph_name_t* n_2 = n_1->copy();
+
+  n_1->merge(5);
+  printf("\nmerge 5:            "); print(n_1);
+
+  n_1->split(3);
+  printf("\nsplit 3:            "); print(n_1);
+
+  n_1->split(0);
+  printf("\nsplit 0:            "); print(n_1);
+
+  n_1->merge(3);
+  printf("\nmerge 3:            "); print(n_1);
+
+  printf("\ncopy*:              "); print(n_2);
+
+  printf("\nhashes are: %ld %ld\n", n_1->hash(), n_2->hash());
+
+  if (n_1->hash() == n_2->hash()) {
+     printf("initial copy's hash equal to previous graph's hash\n");
+  } else {
+    printf("initial copy's hash not equal to previous graph's hash\n");
+  }
+}

### 2021-06-03 v5/tests/graph_test.cpp

@@ -1,0 +1,122 @@
+#include "../classical/rules.hpp"
+#include "../classical/graph.hpp"
+
+int main() {
+  printf("A graphs is inputed by a series of ndoes, having particules (`>` for right and `<` for left) or not.\n");
+  printf("With nodes being separated by a '-'.\n");
+  printf("you can also input 'r' to create a random graph of size 6\n");
+  printf("For exemple the graph:\n    >-<>--<\nis read as:\n    -| |0|>|--|<|1|>|--| |2| |--|<|3| |-\n");
+
+  while (true) {
+    printf("\n----------------------------------------------------\n\nPleas enter next graph (Ctrl+C to exit):\n");
+
+    std::vector<bool> left, right;
+    graph_t* g_1;
+
+    bool l = false;
+    bool r = false;
+
+    while (true) {
+      switch (std::getchar()) {
+        case '<':
+          l = true;
+          break;
+
+        case '>':
+          r = true;
+          break;
+
+        case '-':
+          left.push_back(l);
+          right.push_back(r);
+          l = false;
+          r = false;
+          break;
+
+        case '\n':
+          left.push_back(l);
+          right.push_back(r);
+          l = false;
+          r = false;
+          goto read;
+
+        case 'r':
+          while(std::getchar() != '\n') { }
+          goto random;
+
+        default:
+          return -1;
+      }
+    }
+
+read:
+    g_1 = new graph(left, right);
+    printf("\nread from input*: "); print(g_1);
+    goto loop;
+
+random:
+    g_1 = new graph(6);
+    printf("new graph(6):     "); print(g_1);
+
+    g_1->randomize();
+    printf("\nrandomize()*:     "); print(g_1);
+
+loop:
+    graph_t* g_2 = g_1->copy();
+
+    //--------------
+
+    g_1->step();
+    printf("\n\nstep():           "); print(g_1);
+
+    //---
+
+    g_1->reversed_step();
+    printf("\nreversed_step():  "); print(g_1);
+
+    //--------------
+
+    auto split_merge = get_split_merge(g_1);
+    printf("\n\n"); print_split_merge(split_merge);
+
+    g_1->split_merge(split_merge);
+    printf("\nmerge_split():    "); print(g_1);
+
+    //---
+
+    split_merge = get_split_merge(g_1);
+    printf("\n"); print_split_merge(split_merge);
+
+    g_1->split_merge(split_merge);
[…]

### 2021-06-03 v5/tests/quantum_injectivity_test.cpp

@@ -1,0 +1,149 @@
+#include "../classical/rules.hpp"
+#include "../classical/graph.hpp"
+#include "../quantum/rules.hpp"
+#include "../quantum/state.hpp"
+#include "../quantum/checks.hpp"
+
+#define _USE_MATH_DEFINES
+#include <cmath>
+
+int main() {
+	printf("A graphs is inputed by a series of ndoes, having particules (`>` for right and `<` for left) or not.\n");
+	printf("With nodes being separated by a '-'.\n");
+	printf("you can also input 'r' to create a random graph of size 6\n");
+	printf("For exemple the graph:\n    >-<>--<\nis read as:\n    -| |0|>|--|<|1|>|--| |2| |--|<|3| |-\n");
+
+	while (true) {
+		printf("\n----------------------------------------------------\n\nPleas enter next graph (Ctrl+C to exit):\n");
+
+		std::vector<bool> left, right;
+	    graph_t* g_1;
+
+	    bool l = false;
+	    bool r = false;
+
+	    while (true) {
+	    	switch (std::getchar()) {
+	      		case '<':
+	      			l = true;
+	      			break;
+
+	      		case '>':
+	      			r = true;
+	      			break;
+
+	      		case '-':
+	      			left.push_back(l);
+	      			right.push_back(r);
+	      			l = false;
+	      			r = false;
+	      			break;
+
+	      		case '\n':
+	      			left.push_back(l);
+	      			right.push_back(r);
+	      			l = false;
+	      			r = false;
+	      			goto read;
+
+	      		case 'r':
+	      			while(std::getchar() != '\n') { }
+	      			goto random;
+
+	      		default:
+	      			return -1;
+	    	}
+	    }
+
+read:
+    	g_1 = new graph(left, right);
+    	printf("\nread from input*: "); print(g_1);
+    	goto loop;
+
+random:
+    	g_1 = new graph(6);
+    	printf("new graph(6):  "); print(g_1);
+
+    	g_1->randomize();
+    	printf("\nrandomize()*:  "); print(g_1); printf("\n");
+
+loop:
+
+		state_t* s = new state(g_1);
+	    auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
+
+	    auto rule = step_split_merge_all(non_merge, merge);
+	    auto reversed_rule = reversed_step_split_merge_all(non_merge, merge);
+
[…]

### 2021-06-03 v5/tests/quantum_iteration.cpp

@@ -8,11 +8,10 @@
 #include <cmath>
 
 int main() {
-    graph_t* g_1 = new graph(5, {0, 3},  {0, 2, 4});
+    graph_t* g_1 = new graph({true, false, false, true, false},  {true, false, true, false, true});
 
-    /*graph_t* g_1 = new graph(4);
-    //g_1->randomize();
-    g_1->randomize(3);*/
+    /*graph_t* g_1 = new graph(7);
+    g_1->randomize();*/
 
     print(g_1);
 

### 2021-06-03 v5/tests/state_test.cpp

@@ -1,0 +1,102 @@
+#include "../classical/rules.hpp"
+#include "../classical/graph.hpp"
+#include "../quantum/rules.hpp"
+#include "../quantum/state.hpp"
+#include "../quantum/checks.hpp"
+
+#define _USE_MATH_DEFINES
+#include <cmath>
+
+int main() {
+	printf("A graphs is inputed by a series of ndoes, having particules (`>` for right and `<` for left) or not.\n");
+	printf("With nodes being separated by a '-'.\n");
+	printf("you can also input 'r' to create a random graph of size 6\n");
+	printf("For exemple the graph:\n    >-<>--<\nis read as:\n    -| |0|>|--|<|1|>|--| |2| |--|<|3| |-\n");
+
+	while (true) {
+		printf("\n----------------------------------------------------\n\nPleas enter next graph (Ctrl+C to exit):\n");
+
+		std::vector<bool> left, right;
+	    graph_t* g_1;
+
+	    bool l = false;
+	    bool r = false;
+
+	    while (true) {
+	    	switch (std::getchar()) {
+	      		case '<':
+	      			l = true;
+	      			break;
+
+	      		case '>':
+	      			r = true;
+	      			break;
+
+	      		case '-':
+	      			left.push_back(l);
+	      			right.push_back(r);
+	      			l = false;
+	      			r = false;
+	      			break;
+
+	      		case '\n':
+	      			left.push_back(l);
+	      			right.push_back(r);
+	      			l = false;
+	      			r = false;
+	      			goto read;
+
+	      		case 'r':
+	      			while(std::getchar() != '\n') { }
+	      			goto random;
+
+	      		default:
+	      			return -1;
+	    	}
+	    }
+
+read:
+    	g_1 = new graph(left, right);
+    	printf("\nread from input*: "); print(g_1);
+    	goto loop;
+
+random:
+    	g_1 = new graph(6);
+    	printf("new graph(6):  "); print(g_1);
+
+    	g_1->randomize();
+    	printf("\nrandomize()*:  "); print(g_1); printf("\n");
+
+loop:
+
+		state_t* s = new state(g_1);
+		auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
+    	auto rule = split_merge_all(non_merge, merge);
+    	auto rule_ = erase_create_all(non_merge, merge);
+
+		s->step_all(rule);
[…]

### 2021-06-03 v4/tests/quantum_iteration.cpp
updated the new version

@@ -8,7 +8,7 @@
 #include <cmath>
 
 int main() {
-    graph_t* g_1 = new graph(5, {0, 3},  {0, 2, 4});
+    graph_t* g_1 = new graph(5, {0, 3, 4},  {0, 2, 4});
 
     /*graph_t* g_1 = new graph(4);
     //g_1->randomize();
@@ -18,9 +18,9 @@ int main() {
 
     state_t* s = new state(g_1);
     auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
-    auto rule = /*step_split_merge_all*/step_erase_create_all(non_merge, merge);
+    auto rule = /*step_split_merge_all*/split_merge_step_erase_create_all/**/(non_merge, merge);
 
-    for (int i = 1; i < 11; ++i) {
+    for (int i = 1; i < 5; ++i) {
 
         printf("%ld graph", s->graphs().size());
         #ifdef VERBOSE

### 2021-06-03 v5/classical/graph.hpp

@@ -86,11 +86,17 @@ public:
   	void inline erase_create(std::vector<op_t>& erase_create); //indexes have to be sorted !!
 
   	// step function 
-  	void inline step();
+  	void inline step() {
+  		hashed_ = false;
+
+  		std::rotate(left.begin(), left.begin() + 1, left.end());
+		std::rotate(right.rbegin(), right.rbegin() + 1, right.rend());
+  	}
   	void inline reversed_step() {
-  		std::swap(left, right);
-  		step();
-  		std::swap(left, right);
+  		hashed_ = false;
+  		
+  		std::rotate(left.rbegin(), left.rbegin() + 1, left.rend());
+		std::rotate(right.begin(), right.begin() + 1, right.end());
   	}
 };
 
@@ -128,20 +134,6 @@ size_t graph::hash() const {
 
   hashed_ = true;
   return hash_;
-}
-
-//step
-void inline graph::step() {
-	hashed_ = false;
-
-	// step right particules
-	bool previous = right.back();
-	for (int i = 0; i < size(); ++i)
-		swap(right[i], previous);
-
-	previous = left[0];
-	for (int i = size() - 1; i >= 0; --i)
-		swap(left[i], previous);
 }
 
 // split merge 

### 2021-06-03 v5/tests/quantum_iteration.cpp

@@ -8,7 +8,7 @@
 #include <cmath>
 
 int main() {
-    graph_t* g_1 = new graph({true, false, false, true, false},  {true, false, true, false, true});
+    graph_t* g_1 = new graph({true, false, false, true, true},  {true, false, true, false, true});
 
     /*graph_t* g_1 = new graph(7);
     g_1->randomize();*/
@@ -17,9 +17,9 @@ int main() {
 
     state_t* s = new state(g_1);
     auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
-    auto rule = /*step_split_merge_all*/step_erase_create_all(non_merge, merge);
+    auto rule = /*step_split_merge_all*/split_merge_step_erase_create_all/**/(non_merge, merge);
 
-    for (int i = 1; i < 11; ++i) {
+    for (int i = 1; i < 5; ++i) {
 
         printf("%ld graph", s->graphs().size());
         #ifdef VERBOSE

### 2021-06-07 v5/classical/rules.hpp
trying to fix a weird memory issue

@@ -3,50 +3,55 @@
 #include "graph.hpp"
 
 // function to get all split and merges 
-std::vector<graph::op_t> inline get_split_merge(graph_t const* graph) {
+std::vector<graph::op_t> inline get_split_merge(graph_t const &graph) {
 	std::vector<graph::op_t> split_merges;
 	
-	auto const size_ = graph->size();
+	auto const size_ = graph.size();
 	for (int i = 0; i < size_; ++i)
-		if (graph->left[i] && graph->right[i]) {
-			split_merges.push_back({i, graph->split_t});
+		if (graph.left[i] && graph.right[i]) {
+			split_merges.push_back({i, graph.split_t});
 		} else {
 			// next pos
 			unsigned short int next_pos = (i + 1) % size_; 
 
-			if (graph->left[i] && graph->right[next_pos] && !graph->left[next_pos])
-				split_merges.push_back({i, graph->merge_t});
+			if (graph.left[i] && graph.right[next_pos] && !graph.left[next_pos])
+				split_merges.push_back({i, graph.merge_t});
 		}
 
 	return split_merges;
 }
 
 // split merge a graph
-void split_merge(graph_t* graph) {
-	auto split_merges = get_split_merge(graph);
-	graph->split_merge(split_merges);
+void split_merge(graph_t &graph) {
+	auto split_merges = get_split_merge((graph_t const &)graph);
+	graph.split_merge(split_merges);
 }
 
 //function to get all void and split
-std::vector<graph::op_t> inline get_erase_create(graph_t const* graph) {
+std::vector<graph::op_t> inline get_erase_create(graph_t const &graph) {
 	std::vector<graph::op_t> create_erases;
 
-	for (int i = 0; i < graph->size(); ++i)
-		if (graph->left[i] && graph->right[i]) {
-			create_erases.push_back({i, graph->erase_t});
-		} else if (!graph->left[i] && !graph->right[i])
-			create_erases.push_back({i, graph->create_t});
+	for (int i = 0; i < graph.size(); ++i)
+		if (graph.left[i] && graph.right[i]) {
+			create_erases.push_back({i, graph.erase_t});
+		} else if (!graph.left[i] && !graph.right[i])
+			create_erases.push_back({i, graph.create_t});
 
 	return create_erases;
 }
 
 // erase create a graph
-void erase_create(graph_t* graph) {
-	auto erase_creates = get_erase_create(graph);
-	graph->erase_create(erase_creates);
+void erase_create(graph_t &graph) {
[…]

### 2021-06-07 v5/grapher/classical_iteration.cpp

@@ -2,11 +2,14 @@
 #include "../classical/graph.hpp"
 #include "../classical/checks.hpp"
 
-const int n_iteration = 1000;
 const int n_iter = 20;
 
+#ifndef N_ITER
+    #define N_ITER 10000
+#endif
+
 int main() {
-  std::vector<float> sizes(2*n_iteration + 1, 0);
+  std::vector<float> sizes(2*N_ITER + 1, 0);
 
   for (int j = 0; j < n_iter - 1; ++j) {
     graph_t* g = new graph(50);
@@ -14,15 +17,15 @@ int main() {
 
     graph_t* g_0 = g->copy();
 
-    for (int i = n_iteration - 1; i >= 0; --i) {
+    for (int i = N_ITER - 1; i >= 0; --i) {
       split_merge(g);
       g->reversed_step();
       sizes[i] += g->size() / n_iter;
     }
 
-    sizes[n_iteration] += g_0->size() / n_iter;
+    sizes[N_ITER] += g_0->size() / n_iter;
 
-    for (int i = n_iteration + 1; i < 2*n_iteration + 1; ++i) {
+    for (int i = N_ITER + 1; i < 2*N_ITER + 1; ++i) {
       g_0->step();
       split_merge(g_0);
       sizes[i] += g_0->size() / n_iter;

### 2021-06-07 v5/quantum/rules.hpp

@@ -49,7 +49,7 @@ std::pair<std::complex<long double>, std::complex<long double>> unitary(long dou
 // split merge a graph
 auto split_merge_all(std::complex<long double>& non_merge, std::complex<long double>& merge) {
 	return [&](std::shared_ptr<graph_t> const &g) {
-		auto split_merge = get_split_merge(g.get());
+		auto split_merge = get_split_merge(*g);
 		tbb::concurrent_vector<std::pair<std::shared_ptr<graph_t>, std::complex<long double>>> graphs;
 
 		#pragma omp parallel
@@ -81,7 +81,7 @@ auto split_merge_all(std::complex<long double>& non_merge, std::complex<long dou
 // split merge a graph
 auto erase_create_all(std::complex<long double>& non_create, std::complex<long double>& create) {
 	return [&](std::shared_ptr<graph_t> const &g) {
-		auto erase_create = get_erase_create(g.get());
+		auto erase_create = get_erase_create(*g);
 		tbb::concurrent_vector<std::pair<std::shared_ptr<graph_t>, std::complex<long double>>> graphs;
 
 		#pragma omp parallel
@@ -160,7 +160,7 @@ auto reversed_step_erase_create_all(std::complex<long double>& non_merge, std::c
 auto split_merge_step_erase_create_all(std::complex<long double>& non_merge, std::complex<long double>& merge) {
 	return [&](std::shared_ptr<graph_t> const &g) {
 		auto const erase_create_all_ = erase_create_all(non_merge, merge);
-		split_merge(g.get());
+		split_merge(*g);
 		g->step();
 		return erase_create_all_(g);
 	};
@@ -169,7 +169,7 @@ auto split_merge_step_erase_create_all(std::complex<long double>& non_merge, std
 auto erase_create_step_split_merge_all(std::complex<long double>& non_merge, std::complex<long double>& merge) {
 	return [&](std::shared_ptr<graph_t> const &g) {
 		auto const split_merge_all_ = split_merge_all(non_merge, merge);
-		erase_create(g.get());
+		erase_create(*g);
 		g->step();
 		return split_merge_all_(g);
 	};

### 2021-06-07 v5/quantum/state.hpp

@@ -173,7 +173,7 @@ void state::step_all(std::function<tbb::concurrent_vector<std::pair<std::shared_
   	for (auto & [graph, mag] : buff)
 	#pragma omp task
   	{
-  		auto graphs = rule(graph);
+  		auto const graphs = rule(graph);
   		for (auto & [graph_, mag_] : graphs)
   		#pragma task
   		{

### 2021-06-07 v5/tests/classical_injectivity_test.cpp

@@ -17,13 +17,13 @@ int main() {
 
       g->step();
       g->reversed_step();
-      split_merge(g);
+      split_merge(*g);
 
       graph_t* c2 = new graph_t(*g);
 
-      split_merge(c2);
-      erase_create(c2);
-      erase_create(c2);
+      split_merge(*c2);
+      erase_create(*c2);
+      erase_create(*c2);
 
       if (c->hash() != c2->hash() /*!g->equal(c)*/){
         print(c2); printf("\n");

### 2021-06-07 v5/tests/graph_test.cpp

@@ -76,7 +76,7 @@ loop:
 
     //--------------
 
-    auto split_merge = get_split_merge(g_1);
+    auto split_merge = get_split_merge(*g_1);
     printf("\n\n"); print_split_merge(split_merge);
 
     g_1->split_merge(split_merge);
@@ -84,7 +84,7 @@ loop:
 
     //---
 
-    split_merge = get_split_merge(g_1);
+    split_merge = get_split_merge(*g_1);
     printf("\n"); print_split_merge(split_merge);
 
     g_1->split_merge(split_merge);
@@ -92,7 +92,7 @@ loop:
 
     //--------------
 
-    auto erase_create = get_erase_create(g_1);
+    auto erase_create = get_erase_create(*g_1);
     printf("\n\n"); print_erase_create(erase_create);
     
     g_1->erase_create(erase_create);
@@ -100,7 +100,7 @@ loop:
 
     //---
 
-    erase_create = get_erase_create(g_1);
+    erase_create = get_erase_create(*g_1);
     printf("\n"); print_erase_create(erase_create);
     
     g_1->erase_create(erase_create);

### 2021-06-07 v5/tests/quantum_injectivity_test.cpp

@@ -7,6 +7,18 @@
 #define _USE_MATH_DEFINES
 #include <cmath>
 
+#ifndef N_ITER
+    #define N_ITER 20
+#endif
+
+#ifndef TETA
+    #define TETA M_PI_4
+#endif
+
+#ifndef PHI
+    #define PHI M_PI_2
+#endif
+
 int main() {
 	printf("A graphs is inputed by a series of ndoes, having particules (`>` for right and `<` for left) or not.\n");
 	printf("With nodes being separated by a '-'.\n");
@@ -70,14 +82,12 @@ random:
 loop:
 
 		state_t* s = new state(g_1);
-	    auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
+	    auto [non_merge, merge] = unitary(TETA, PHI);
 
 	    auto rule = step_split_merge_all(non_merge, merge);
 	    auto reversed_rule = reversed_step_split_merge_all(non_merge, merge);
 
-		int n_iter = 6;
-
-		for (int i = 0; i < n_iter; ++i) {
+		for (int i = 0; i < N_ITER; ++i) {
 			s->step_all(rule);
 			s->reduce_all();
 
@@ -93,9 +103,9 @@ loop:
 		
 		printf("%ld graph of size ", s->graphs().size());
         size_stat(s);
-        printf(" after %d step_merge_split()\n", n_iter);
+        printf(" after %d step_merge_split()\n", N_ITER);
 
-		for (int i = 0; i < n_iter; ++i) {
+		for (int i = 0; i < N_ITER; ++i) {
 			s->step_all(reversed_rule);
 			s->reduce_all();
 
@@ -107,14 +117,14 @@ loop:
 			#endif
 		}
 
-		printf("\nafter %d reversed_step_merge_split():\n", n_iter); print(s);
+		printf("\nafter %d reversed_step_merge_split():\n", N_ITER); print(s);
 
 		//--------------------------
 
 		auto rule_ = step_erase_create_all(non_merge, merge);
 	    auto reversed_rule_ = reversed_step_erase_create_all(non_merge, merge);
 
-		for (int i = 0; i < n_iter; ++i) {
+		for (int i = 0; i < N_ITER; ++i) {
 			s->step_all(rule_);
 			s->reduce_all();
 
@@ -130,9 +140,9 @@ loop:
 		
         printf("%ld graph of size ", s->graphs().size());
         size_stat(s);
[…]

### 2021-06-07 v5/tests/quantum_iteration.cpp

@@ -7,6 +7,18 @@
 #define _USE_MATH_DEFINES
 #include <cmath>
 
+#ifndef N_ITER
+    #define N_ITER 20
+#endif
+
+#ifndef TETA
+    #define TETA M_PI_4
+#endif
+
+#ifndef PHI
+    #define PHI M_PI_2
+#endif
+
 int main() {
     graph_t* g_1 = new graph({true, false, false, true, true},  {true, false, true, false, true});
 
@@ -16,10 +28,10 @@ int main() {
     print(g_1);
 
     state_t* s = new state(g_1);
-    auto [non_merge, merge] = unitary(M_PI_4, M_PI_2);
+    auto [non_merge, merge] = unitary(TETA, PHI);
     auto rule = /**/step_split_merge_all/*step_erase_create_all*/(non_merge, merge);
 
-    for (int i = 1; i < 10; ++i) {
+    for (int i = 1; i < N_ITER; ++i) {
 
         printf("%ld graph", s->graphs().size());
         #ifdef VERBOSE

### 2021-06-07 v5/paper/paper.tex
adding debuging print to find the memory error

--- 2021-06-02 paper/paper.tex
@@
 class graph {
+	// split_merge type enum 
+  	typedef enum op_type {
+		split_t,
+		merge_t,
+		erase_t,
+		create_t,
+	} op_type_t;
+
+	// typedef of the pair of an index and a op_type 
+  	typedef std::pair<unsigned int, op_type_t> op_t;
+
 	// variables 
-	graph_name_t* name_;
-	std::vector<unsigned int> left_;
-	std::vector<unsigned int> right_;
+	graph_name_t name_;
+	std::vector<char /*bool*/> left;
+	std::vector<char /*bool*/> right;
 
@@
 
-The fonction to step all particules uses the fonctions "rotate\_once\_left" and "rotate\_once\_right" which rotate particules if they overflow:
-
 \begin{lstlisting}[style=CStyle]
@@
 
-  		rotate_once_right(right_);
-  		rotate_once_left(left_);
+  		std::rotate(left.begin(), left.begin() + 1, left.end());
+		std::rotate(right.rbegin(), right.rbegin() + 1, right.rend());
   	}
@@
 
-  		rotate_once_right(left_);
-  		rotate_once_left(right_);
+  		std::rotate(left.rbegin(), left.rbegin() + 1, left.rend());
+		std::rotate(right.begin(), right.begin() + 1, right.end());
   	}
@@
 
-		// check for last merge
-		if (split_merge.back() == split_merge_t(size() - 1, merge_t)) {
-			name_->merge(size() - 1);
-			overflow_right(left_);	
-			split_merge.pop_back();
+		bool first_split = false;
+		auto const size_ = size();
+		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
+			if (type == split_t) {
+				first_split |= name_.split(pos);
+
+				// change right
+				right[pos] = false;
+
+				//insert
+				right.insert(right.begin() + pos + 1, true);
+				left.insert(left.begin() + pos + 1, false);
+			} else if (type == merge_t) {
+				name_.merge(pos);
+
+				// next pos
+				unsigned short int next_pos = (pos + 1) % size_;
+
+				// change left
+				left[next_pos] = true;
+
+				//erase
+				right.erase(right.begin() + pos);
+				left.erase(left.begin() + pos);
 			}
 
-		// check for first element split 
-		bool first_split = false;
+		/* finish first split */
+		if (first_split) {
+			std::rotate(left.begin(), left.begin() + 1, left.end());
+			std::rotate(right.begin(), right.begin() + 1, right.end());
+		}
+	}
+	//...
+\end{lstlisting}
 
-		// and calculating max displacement 
-		int total_displacement = 0;
-		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
-			if (type == split_t) {
-				++total_displacement;
-			} else
-				--total_displacement;
+\subsubsection{erase\_create()}
 
-		// reserve space for nodes
-		name_->reserve(total_displacement);
+\begin{lstlisting}[style=CStyle]
 
-		// split and merge names
-		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
-			if (type == split_t) {
-				first_split |= name_->split(pos);
-			} else
-				name_->merge(pos);
+void inline graph::erase_create(std::vector<op_t>& erase_create) {
+	//...
+	void inline erase_create(std::vector<op_t>& erase_create) {
+		if (erase_create.empty())
+			return;
 
-		// move particules
-		auto const split_merge_begin = split_merge.rend();
-		int displacement = total_displacement;
-		auto split_merge_it = split_merge.rbegin();
-		for (auto &left_it : left_ | std::ranges::views::reverse) {
-			// check if there are any nodes left
-			for (;split_merge_it->first >= left_it && split_merge_it != split_merge_begin; ++split_merge_it)
-				// check if the node is split or merged
-				if (split_merge_it->second == split_t) {
-						--displacement; // decrement the displacement 
-					} else
-						++displacement; // decrement the displacement
+		hashed_ = false;
 
-			//check if we can exit
-			if (split_merge_it == split_merge_begin && displacement == 0)
-				break;
-
-			left_it += displacement;
-		}
-
-		/* we than do the exact same thing with particule going to the right, rplacing ">=" at line 42 by a ">" */
-
-		// finish first split 
-		if (first_split) {
-			rotate_once_left(left_);
-			rotate_once_left(right_);
+		for (auto & [pos, type] : erase_create)
+			if (type == erase_t) {
+				left[pos] = false;
+				right[pos] = false;
+			} else if (type == create_t) {
+				left[pos] = true;
+				right[pos] = true;
 			}
@@
 
+		// save memory 
+		left.shrink_to_fit();
+		right.shrink_to_fit();
+
 		hash_ = 0;
@@
 		// left hash 
-		for (auto &l : left_)
-			boost::hash_combine(hash_, l);
+		auto const size_ = size();
+		for (short int i = 0; i < size_; ++i)
+			if (left[i])
+				boost::hash_combine(hash_, i);
 
@@
 	  	// right hash 
-	  	for (auto &r : right_)
-	   		boost::hash_combine(hash_, r);
+	  	for (short int i = 0; i < size_; ++i)
+			if (right[i])
+				boost::hash_combine(hash_, i);
 
@@
 	  	// name hash 
-	  	boost::hash_combine(hash_, name_->hash());
+	  	boost::hash_combine(hash_, name_.hash());
 
@@
 
-To get the list of all indeces of splits and merges, we iterate through both the "left" and "right" positions, iterating the one that is the smallest so that it always converges towars positions that match (or are one apart for merges):
-
 \begin{lstlisting}[style=CStyle]
@@
 std::vector<graph::split_merge_t> inline get_split_merge(graph_t* graph) {
-	std::vector<graph::op_t> split_merge;
+	std::vector<graph::op_t> split_merges;
 
-	unsigned int const last_idx = graph->size() - 1;
+	auto const size_ = graph.size();
+	for (int i = 0; i < size_; ++i)
+		if (graph.left[i] && graph.right[i]) {
+			split_merges.push_back({i, graph.split_t});
+		} else {
+			// next pos
+			unsigned short int next_pos = (i + 1) % size_;
 
-	auto left_it = graph->left().begin();
-	auto right_it = graph->right().begin();
-	bool first_or_last_split = *left_it == *right_it && *left_it == 0;
-	first_or_last_split |= graph->left().back() == last_idx && graph->right().back() == last_idx;
+			if (graph.left[i] && graph.right[next_pos] && !graph.left[next_pos])
+				split_merges.push_back({i, graph.merge_t});
+		}
 
-	while (right_it < right_end = graph->right().end() && left_it < graph->left().end())
-		if (*left_it == *right_it) {
-			// check for split
-			split_merge.push_back({*left_it, graph->split_t});
+	return split_merges;
+}
+\end{lstlisting}
 
-			++right_it;
-			++left_it;
-		} else if (*left_it < *right_it) {
-			// chedk for merges
-			if (*left_it == *right_it - 1)
-				if (left_it == graph->left().end() - 1) {
-					split_merge.push_back({*left_it, graph->merge_t});
-				} else if (*(left_it + 1) != *right_it)
-					split_merge.push_back({*left_it, graph->merge_t});
+\subsubsection{get\_erase\_create()}
 
-			++left_it;
-		} else
-			++right_it;
+\begin{lstlisting}[style=CStyle]
+std::vector<graph::op_t> inline get_erase_create(graph_t const &graph) {
+	std::vector<graph::op_t> create_erases;
 
-	if (!first_or_last_split)
-		if (graph->left().back() == last_idx && graph->right()[0] == 0)
-			split_merge.push_back({last_idx, graph->merge_t});
+	for (int i = 0; i < graph.size(); ++i)
+		if (graph.left[i] && graph.right[i]) {
+			create_erases.push_back({i, graph.erase_t});
+		} else if (!graph.left[i] && !graph.right[i])
+			create_erases.push_back({i, graph.create_t});
 
-	return split_merge;
+	return create_erases;
 }
@@
 	void reduce_all() {
-		for(auto it = graphs_.begin(); it != graphs_.end();) {
+		graph_map_t buff; // faster, parallel reduce that uses WAY more ram
+		buff.swap(graphs_);
+
+		#pragma omp parallel
+		#pragma omp single
+	    for(auto it = buff.begin(); it != buff.end();) {
 	    	// range of similar graphs to delete
-			auto upper = graphs_.equal_range(it->first).second;
+	    	auto const graph = it->first;
+	    	auto const range = buff.equal_range(graph);
 
-			for(auto jt = std::next(it); jt != upper; ++jt)
-		    	it->second += jt->second;
+	    	// next iteration
+	    	it = range.second;
+
+	    	#pragma omp task
+	    	{
+	    		std::complex<long double> acc = 0;
+	    		for(auto jt = range.first; jt != range.second; ++jt)
+	        		acc += jt->second;
 
 		    	// if the first graphgs has a zero probability, erase the whole range
-			if (!check_zero(it->second))
-				++it;
-
-			it = graphs_.unsafe_erase(it, upper);
+		    	if (!check_zero(acc))
+		    		graphs_.insert({graph, acc});
+	    	}
 	    }
@@
 		{
-			auto graphs = rule(graph);
+			auto const graphs = rule(graph);
 			for (auto & [graph_, mag_] : graphs)

### 2021-06-07 v5/classical/graph.hpp

@@ -114,8 +114,8 @@ size_t graph::hash() const {
   	// name hash 
   	boost::hash_combine(hash_, name_.hash());
 		
-  hashed_ = true;
-  return hash_;
+  	hashed_ = true;
+  	return hash_;
 }
 
 // split merge 

### 2021-06-07 v5/grapher/quantum_iteration.cpp

@@ -81,11 +81,11 @@ int main() {
     
     for (int i = 1; i < N_ITER + 1; ++i) {
         if (rule2_) {
-            s->step_all(rule2);
+            printf("step...\n"); s->step_all(rule2); printf("...OK\n"); //supecting errors here
             s->reduce_all();
         }
 
-        s->step_all(rule);
+        printf("step...\n"); s->step_all(rule); printf("...OK\n"); //supecting errors here
         s->reduce_all();
 
         if (MAX_NUM_GRAPHS > 0)

### 2021-06-07 v5/quantum/state.hpp

@@ -25,7 +25,9 @@ public:
 	// comparator
 	struct graph_comparator {
 		bool operator()(std::shared_ptr<graph_t> const &g1, std::shared_ptr<graph_t> const &g2) const {
-			#ifdef SLOW_COMPARE
+			#ifndef SLOW_COMPARE
+				return g1->hash() == g2->hash();
+			#else
 				if (g1->left != g2->left)
 					return false;
 
@@ -37,8 +39,6 @@ public:
 						return false;
 
 				return true;
-			#else
-				return g1->hash() == g2->hash();
 			#endif
 		}
 	};
@@ -82,21 +82,7 @@ void state::reduce_all() {
 		printf("reducing %ld graphs...\n", graphs_.size());
 	#endif
 
-    #ifdef SLOW_REDUCE
-		for(auto it = graphs_.begin(); it != graphs_.end();) {
-	    	// range of similar graphs to delete
-	    	auto upper = graphs_.equal_range(it->first).second;
-
-	    	for(auto jt = std::next(it); jt != upper; ++jt)
-	        	it->second += jt->second;
-
-	    	// if the first graphgs has a zero probability, erase the whole range
-	    	if (!check_zero(it->second))
-	    		++it;
-	    	
-	    	it = graphs_.unsafe_erase(it, upper);
-	    }
-    #else
+    #ifndef SLOW_REDUCE
 		graph_map_t buff; // faster, parallel reduce that uses WAY more ram
 		buff.swap(graphs_);
 
@@ -120,6 +106,20 @@ void state::reduce_all() {
 		    	if (!check_zero(acc))
 		    		graphs_.insert({graph, acc});
 	    	}
+	    }
+    #else
+		for(auto it = graphs_.begin(); it != graphs_.end();) {
+	    	// range of similar graphs to delete
+	    	auto upper = graphs_.equal_range(it->first).second;
+
+	    	for(auto jt = std::next(it); jt != upper; ++jt)
+	        	it->second += jt->second;
+
+	    	// if the first graphgs has a zero probability, erase the whole range
+	    	if (!check_zero(it->second))
+	    		++it;
+	    	
+	    	it = graphs_.unsafe_erase(it, upper);
 	    }
     #endif
 }
@@ -174,11 +174,19 @@ void state::step_all(std::function<tbb::concurrent_vector<std::pair<std::shared_
 	#pragma omp task
   	{
   		auto const graphs = rule(graph);
+
+  		#pragma omp barrier
[…]

### 2021-06-07 v5/quantum/state.hpp
adding debuging print to find the memory error

@@ -168,25 +168,22 @@ void state::step_all(std::function<tbb::concurrent_vector<std::pair<std::shared_
 	graph_map_t buff;
 	buff.swap(graphs_);
 
-	#pragma omp parallel
-	#pragma omp single
+	//#pragma omp parallel
+	//#pragma omp single
   	for (auto & [graph, mag] : buff)
-	#pragma omp task
+	//#pragma omp task
   	{
+  		printf(" a");
   		auto const graphs = rule(graph);
-
-  		#pragma omp barrier
-  		if (graph.hash() == buff.begin()->first.hash())
-  			printf("created graphs..\n"); // suspecting error here
+  		printf("b ");
 
   		for (auto & [graph_, mag_] : graphs)
-  		#pragma task
-  		{
+  		//#pragma task
+  		{	
+  			printf(" c");
   			graphs_.insert({graph_, mag_ * mag});
+  			printf("d ");
   		}
-  		#pragma omp barrier
-  		if (graph.hash() == buff.begin()->first.hash())
-  			printf("..OK\n"); // suspecting error here
   	}
 }
 

### 2021-06-07 v5/classical/checks.hpp
changed graph_t to a non-pointer type in functions, and still trying to fix the memory bug

@@ -3,6 +3,6 @@
 #include "graph.hpp"
 
 /* to check */
-bool inline graph_checker(graph_t* graph) {
+bool inline graph_checker(graph_t const &graph) {
 	return true;
 }

### 2021-06-07 v5/classical/graph.hpp

@@ -35,7 +35,9 @@ private:
 	bool mutable hashed_ = false;
 
 public:
-	// normal constructors 
+	// normal constructors
+	graph() {}
+
 	graph(short int n) {
 		left = std::vector<char /*bool*/>(n, false);
 		right = std::vector<char /*bool*/>(n, false);
@@ -191,14 +193,14 @@ void graph::randomize() {
 //---------------------------------------------------------
 
 // debuging 
-void print(graph_t const *g) {
+void print(graph_t const &g) {
 	// iterate through particules positions 
-	auto left_it = g->left.begin();
-	auto right_it = g->right.begin();
+	auto left_it = g.left.begin();
+	auto right_it = g.right.begin();
 
-	for(unsigned short int i = 0; i < g->size(); ++i) {
-		printf("-|%c|", g->left[i] ? '<' : ' ');
-		print(g->name(), i);
-		printf("|%c|-", g->right[i] ? '>' : ' ');
+	for(unsigned short int i = 0; i < g.size(); ++i) {
+		printf("-|%c|", g.left[i] ? '<' : ' ');
+		print(g.name(), i);
+		printf("|%c|-", g.right[i] ? '>' : ' ');
 	}
 }

### 2021-06-07 v5/grapher/classical_iteration.cpp

@@ -12,23 +12,23 @@ int main() {
   std::vector<float> sizes(2*N_ITER + 1, 0);
 
   for (int j = 0; j < n_iter - 1; ++j) {
-    graph_t* g = new graph(50);
-    g->randomize(4);
+    graph_t g = graph_t(50);
+    g.randomize();
 
-    graph_t* g_0 = g->copy();
+    graph_t g_0 = g;
 
     for (int i = N_ITER - 1; i >= 0; --i) {
       split_merge(g);
-      g->reversed_step();
-      sizes[i] += g->size() / n_iter;
+      g.reversed_step();
+      sizes[i] += g.size() / n_iter;
     }
 
-    sizes[N_ITER] += g_0->size() / n_iter;
+    sizes[N_ITER] += g_0.size() / n_iter;
 
     for (int i = N_ITER + 1; i < 2*N_ITER + 1; ++i) {
-      g_0->step();
+      g_0.step();
       split_merge(g_0);
-      sizes[i] += g_0->size() / n_iter;
+      sizes[i] += g_0.size() / n_iter;
     }
   }
 

### 2021-06-07 v5/grapher/quantum_iteration.cpp

@@ -42,8 +42,8 @@
 int main() {
     //graph_t* g_1 = new graph({true, false, false, true, false},  {true, false, true, false, true});
     
-    graph_t* g_1 = new graph(SIZE);
-    g_1->randomize();
+    graph_t g_1 = graph_t(SIZE);
+    g_1.randomize();
 
     state_t* s = new state(g_1);
     s->tolerance = TOLERANCE;

### 2021-06-07 v5/quantum/checks.hpp

@@ -23,7 +23,7 @@ bool check(state_t* s) {
 		}*/
 
 		//check graph
-		if (!graph_checker(it->first.get()))
+		if (!graph_checker(*it->first))
 			return false;
 
     	//iterate over all graphs

### 2021-06-07 v5/quantum/state.hpp

@@ -55,9 +55,9 @@ private:
 
 public:
 	// single graph constructor 
-	state(graph_t* g) {
+	state(graph_t &g) {
 		// add graph 
-		graphs_.insert({std::shared_ptr<graph_t>(g), {1, 0}});
+		graphs_.insert({std::shared_ptr<graph_t>(&g), {1, 0}});
 	}
 
 	//getter
@@ -168,22 +168,16 @@ void state::step_all(std::function<tbb::concurrent_vector<std::pair<std::shared_
 	graph_map_t buff;
 	buff.swap(graphs_);
 
-	//#pragma omp parallel
-	//#pragma omp single
+	#pragma omp parallel
+	#pragma omp single
   	for (auto & [graph, mag] : buff)
-	//#pragma omp task
+	#pragma omp task
   	{
-  		printf(" a");
   		auto const graphs = rule(graph);
-  		printf("b ");
 
   		for (auto & [graph_, mag_] : graphs)
   		//#pragma task
-  		{	
-  			printf(" c");
   			graphs_.insert({graph_, mag_ * mag});
-  			printf("d ");
-  		}
   	}
 }
 
@@ -212,22 +206,22 @@ void size_stat(state_t* s) {
 	printf("%Lf±%Lf", avg, var);
 }
 
-void start_json(graph_t const* initial, char const* rule) {
+void start_json(graph_t const &initial, char const* rule) {
 	// print rule
 	printf("{\n\t\"rule\" : \"%s\",", rule);
 
 	// print initial state staitisic
 	printf("\n\t\"initial state\" : {\n");
-	printf("\t\t\"size\" : %ld\n", initial->size());
+	printf("\t\t\"size\" : %ld\n", initial.size());
 	printf("\t},\n\t\"iterations\" : [");
 
 	// print first iteration statistic
 	printf("\n\t\t{\n\t\t\t\"nums\" : [");
-	for (int i = 0; i < initial->size(); ++i)
+	for (int i = 0; i < initial.size(); ++i)
 		printf("0, ");
 
 	printf("1],\n\t\t\t\"probas\" : [");
-	for (int i = 0; i < initial->size(); ++i)
+	for (int i = 0; i < initial.size(); ++i)
 		printf("0.0, ");
 
 	printf("1.0]\n\t\t}");
@@ -278,7 +272,7 @@ void print(state_t *s) {
 	  	} else {
[…]

### 2021-06-07 v5/tests/classical_injectivity_test.cpp

@@ -9,23 +9,23 @@ int main() {
   #pragma omp task
   {
     
-    graph_t* g = new graph(10);
+    graph_t g = graph_t(10);
 
     for (int i = 0; i < 20; ++i) {
-      g->randomize();
-      graph_t* c = new graph_t(*g);
+      g.randomize();
+      graph_t c = g;
 
-      g->step();
-      g->reversed_step();
-      split_merge(*g);
+      g.step();
+      g.reversed_step();
+      split_merge(g);
 
-      graph_t* c2 = new graph_t(*g);
+      graph_t c2 = g;
 
-      split_merge(*c2);
-      erase_create(*c2);
-      erase_create(*c2);
+      split_merge(c2);
+      erase_create(c2);
+      erase_create(c2);
 
-      if (c->hash() != c2->hash() /*!g->equal(c)*/){
+      if (c.hash() != c2.hash() /*!g->equal(c)*/){
         print(c2); printf("\n");
         print(c); printf("\n");
         throw;

### 2021-06-07 v5/tests/graph_test.cpp

@@ -11,7 +11,7 @@ int main() {
     printf("\n----------------------------------------------------\n\nPleas enter next graph (Ctrl+C to exit):\n");
 
     std::vector<char /*bool*/> left, right;
-    graph_t* g_1;
+    graph_t g_1;
 
     bool l = false;
     bool r = false;
@@ -50,69 +50,69 @@ int main() {
     }
 
 read:
-    g_1 = new graph(left, right);
+    g_1 = graph_t(left, right);
     printf("\nread from input*: "); print(g_1);
     goto loop;
 
 random:
-    g_1 = new graph(6);
+    g_1 = graph(6);
     printf("new graph(6):     "); print(g_1);
 
-    g_1->randomize();
+    g_1.randomize();
     printf("\nrandomize()*:     "); print(g_1);
 
 loop:
-    graph_t* g_2 = new graph_t(*g_1);
+    graph_t g_2 = graph_t(g_1);
 
     //--------------
 
-    g_1->step();
+    g_1.step();
     printf("\n\nstep():           "); print(g_1);
 
     //---
 
-    g_1->reversed_step();
+    g_1.reversed_step();
     printf("\nreversed_step():  "); print(g_1);
 
     //--------------
 
-    auto split_merge = get_split_merge(*g_1);
+    auto split_merge = get_split_merge(g_1);
     printf("\n\n"); print_split_merge(split_merge);
 
-    g_1->split_merge(split_merge);
+    g_1.split_merge(split_merge);
     printf("\nmerge_split():    "); print(g_1);
 
     //---
 
-    split_merge = get_split_merge(*g_1);
+    split_merge = get_split_merge(g_1);
     printf("\n"); print_split_merge(split_merge);
 
-    g_1->split_merge(split_merge);
+    g_1.split_merge(split_merge);
     printf("\nmerge_split():    "); print(g_1);
 
     //--------------
 
-    auto erase_create = get_erase_create(*g_1);
+    auto erase_create = get_erase_create(g_1);
     printf("\n\n"); print_erase_create(erase_create);
     
-    g_1->erase_create(erase_create);
+    g_1.erase_create(erase_create);
     printf("\nerase_create():   "); print(g_1);
 
     //---
 
-    erase_create = get_erase_create(*g_1);
+    erase_create = get_erase_create(g_1);
     printf("\n"); print_erase_create(erase_create);
     
-    g_1->erase_create(erase_create);
[…]

### 2021-06-07 v5/tests/quantum_injectivity_test.cpp

@@ -29,7 +29,7 @@ int main() {
 		printf("\n----------------------------------------------------\n\nPleas enter next graph (Ctrl+C to exit):\n");
 
 		std::vector<char /*bool*/> left, right;
-	    graph_t* g_1;
+	    graph_t g_1;
 
 	    bool l = false;
 	    bool r = false;
@@ -68,15 +68,15 @@ int main() {
 	    }
 
 read:
-    	g_1 = new graph(left, right);
+    	g_1 = graph_t(left, right);
     	printf("\nread from input*: "); print(g_1);
     	goto loop;
 
 random:
-    	g_1 = new graph(6);
+    	g_1 = graph_t(6);
     	printf("new graph(6):  "); print(g_1);
 
-    	g_1->randomize();
+    	g_1.randomize();
     	printf("\nrandomize()*:  "); print(g_1); printf("\n");
 
 loop:

### 2021-06-07 v5/tests/quantum_iteration.cpp

@@ -20,7 +20,7 @@
 #endif
 
 int main() {
-    graph_t* g_1 = new graph({true, false, false, true, true},  {true, false, true, false, true});
+    graph_t g_1 = graph_t({true, false, false, true, true},  {true, false, true, false, true});
 
     /*graph_t* g_1 = new graph(7);
     g_1->randomize();*/

### 2021-06-07 v5/tests/state_test.cpp

@@ -17,7 +17,7 @@ int main() {
 		printf("\n----------------------------------------------------\n\nPleas enter next graph (Ctrl+C to exit):\n");
 
 		std::vector<char /*bool*/> left, right;
-	    graph_t* g_1;
+	    graph_t g_1;
 
 	    bool l = false;
 	    bool r = false;
@@ -56,15 +56,15 @@ int main() {
 	    }
 
 read:
-    	g_1 = new graph(left, right);
+    	g_1 = graph_t(left, right);
     	printf("\nread from input*: "); print(g_1);
     	goto loop;
 
 random:
-    	g_1 = new graph(6);
+    	g_1 = graph_t(6);
     	printf("new graph(6):  "); print(g_1);
 
-    	g_1->randomize();
+    	g_1.randomize();
     	printf("\nrandomize()*:  "); print(g_1); printf("\n");
 
 loop:

### 2021-06-07 v5/quantum/state.hpp
the memory bug seems to have been fixed, tho it's not clear if it wasn't just a random limitation of tbb concurent maps with 64 thread

@@ -57,7 +57,7 @@ public:
 	// single graph constructor 
 	state(graph_t &g) {
 		// add graph 
-		graphs_.insert({std::shared_ptr<graph_t>(&g), {1, 0}});
+		graphs_.insert({std::make_shared<graph_t>(g), {1, 0}});
 	}
 
 	//getter

### 2021-06-07 v5/grapher/quantum_iteration.cpp
changed the way quantum_tierations supported multi-rule

@@ -64,28 +64,21 @@ int main() {
     } else
         return -1;
 
-    bool rule2_ = true;
     rule_ = RULE2;
     if (rule_ == "split_merge_all") {
         rule2 = split_merge_all(non_merge, merge);
+        rule_ += "_";
     } if (rule_ == "erase_create_all") {
         rule2 = erase_create_all(non_merge, merge);
-    } else
-        rule2_ = false;
-
-    if (rule2_)
         rule_ += "_";
+    } else
+        rule2 = rule;
 
     rule_ += RULE;
     start_json(g_1, rule_.c_str());
     
     for (int i = 1; i < N_ITER + 1; ++i) {
-        if (rule2_) {
-            printf("step...\n"); s->step_all(rule2); printf("...OK\n"); //supecting errors here
-            s->reduce_all();
-        }
-
-        printf("step...\n"); s->step_all(rule); printf("...OK\n"); //supecting errors here
+        s->step_all(rule);
         s->reduce_all();
 
         if (MAX_NUM_GRAPHS > 0)
@@ -96,6 +89,8 @@ int main() {
         #ifdef NORMALIZE
             s->normalize();
         #endif
+
+        std::swap(rule, rule2);
    	}
 
     end_json();

### 2021-06-07 v5/grapher/quantum_grapher.py
changed the grapher

@@ -10,25 +10,38 @@ with open('res.json') as f:
 n_iterations = len(data["iterations"])
 n_max = max([len(it["nums"]) for it in data["iterations"]])
 
-sizes = np.arange(0, n_max)
-iterations = np.arange(0, n_iterations)
+# lists
 
-iterations, sizes = np.meshgrid(sizes, iterations)
+sizes_list = np.arange(0, n_max)
+iterations_list = np.arange(0, n_iterations)
+
+iterations, sizes = np.meshgrid(sizes_list, iterations_list)
 
 total_proba = np.zeros(n_iterations)
 total_num = np.zeros(n_iterations)
+avg_size = np.zeros(n_iterations)
+std_dev_size = np.zeros(n_iterations)
 
 nums = np.zeros((n_iterations, n_max))
 probas = np.zeros((n_iterations, n_max))
 
+# compute values
+
 for i in range(n_iterations):
+	# compute proba
 	probas_ = data["iterations"][i]["probas"]
 	total_proba[i] = sum(probas_)
 	probas_ /= total_proba[i]
 
+	# compute nums
 	nums_ = data["iterations"][i]["nums"]
 	total_num[i] = sum(nums_)
 	nums_ /= total_num[i]
+
+	#compute sizes
+	sizes_ = np.arange(0, len(nums_))
+	avg_size[i] = sum(probas_ * sizes_)
+	std_dev_size[i] = np.sqrt(abs(avg_size[i] * avg_size[i] - sum(probas_ * sizes_ * sizes_)))
 
 	for j in range(len(nums_)):
 		nums[i, j] = nums_[j]
@@ -73,7 +86,7 @@ fig.savefig(f'plots/proportions/n_{ data["rule"] }_{ data["initial state"]["size
 fig = plt.figure()
 ax = plt.axes()
 ax.set_xlabel('iterations')
-ax.set_title(f'graph probabilty ({ data["rule"] })')
+ax.set_title(f'total probabilty and number of graph ({ data["rule"] })')
 
 color = 'tab:blue'
 color2 = 'tab:red'
@@ -90,3 +103,16 @@ ax2.set_ylabel("total number of graphs", color=color2)
 ax2.tick_params(axis='y', labelcolor=color2)
 
 fig.savefig(f'plots/stats/s_{ data["rule"] }_{ data["initial state"]["size"] }.png')
+
+
+#graph sizes
+
+fig = plt.figure()
+ax = plt.axes()
[…]

### 2021-06-07 v5/grapher/quantum_iteration.cpp

@@ -39,6 +39,14 @@
     #define PHI M_PI_2
 #endif
 
+#ifndef TETA2
+    #define TETA2 TETA
+#endif
+
+#ifndef PHI2
+    #define PHI2 PHI
+#endif
+
 int main() {
     //graph_t* g_1 = new graph({true, false, false, true, false},  {true, false, true, false, true});
     
@@ -48,6 +56,7 @@ int main() {
     state_t* s = new state(g_1);
     s->tolerance = TOLERANCE;
     auto [non_merge, merge] = unitary(TETA, PHI);
+    auto [non_create, create] = unitary(TETA2, PHI2);
 
     std::function<tbb::concurrent_vector<std::pair<std::shared_ptr<graph_t>, std::complex<long double>>>(std::shared_ptr<graph_t> g)> rule;
     std::function<tbb::concurrent_vector<std::pair<std::shared_ptr<graph_t>, std::complex<long double>>>(std::shared_ptr<graph_t> g)> rule2;
@@ -65,11 +74,17 @@ int main() {
         return -1;
 
     rule_ = RULE2;
-    if (rule_ == "split_merge_all") {
-        rule2 = split_merge_all(non_merge, merge);
+    if (rule_ == "step_split_merge_all") {
+        rule = step_split_merge_all(non_create, create);
+        rule_ += "_";
+    } else if (rule_ == "step_erase_create_all") {
+        rule = step_erase_create_all(non_create, create);
+        rule_ += "_";
+    } else if (rule_ == "split_merge_all") {
+        rule2 = split_merge_all(non_create, create);
         rule_ += "_";
     } if (rule_ == "erase_create_all") {
-        rule2 = erase_create_all(non_merge, merge);
+        rule2 = erase_create_all(non_create, create);
         rule_ += "_";
     } else
         rule2 = rule;

### 2021-06-07 v5/grapher/quantum_iteration.cpp
corrected new rules

@@ -75,10 +75,10 @@ int main() {
 
     rule_ = RULE2;
     if (rule_ == "step_split_merge_all") {
-        rule = step_split_merge_all(non_create, create);
+        rule2 = step_split_merge_all(non_create, create);
         rule_ += "_";
     } else if (rule_ == "step_erase_create_all") {
-        rule = step_erase_create_all(non_create, create);
+        rule2 = step_erase_create_all(non_create, create);
         rule_ += "_";
     } else if (rule_ == "split_merge_all") {
         rule2 = split_merge_all(non_create, create);

### 2021-06-07 v5/grapher/quantum_iteration.cpp
corrected errors with multi-rules

@@ -83,7 +83,7 @@ int main() {
     } else if (rule_ == "split_merge_all") {
         rule2 = split_merge_all(non_create, create);
         rule_ += "_";
-    } if (rule_ == "erase_create_all") {
+    } else if (rule_ == "erase_create_all") {
         rule2 = erase_create_all(non_create, create);
         rule_ += "_";
     } else
@@ -93,7 +93,11 @@ int main() {
     start_json(g_1, rule_.c_str());
     
     for (int i = 1; i < N_ITER + 1; ++i) {
-        s->step_all(rule);
+        if (i%2) {
+            s->step_all(rule);
+        } else
+            s->step_all(rule2);
+
         s->reduce_all();
 
         if (MAX_NUM_GRAPHS > 0)
@@ -104,8 +108,6 @@ int main() {
         #ifdef NORMALIZE
             s->normalize();
         #endif
-
-        std::swap(rule, rule2);
    	}
 
     end_json();

### 2021-06-29 raport_de_stage/main.tex
ajouter raport de stage

\documentclass[11pts,french]{article}

\usepackage[utf8]{inputenc}
\usepackage[left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{tikz-qtree}
\usepackage{hyperref}
\usepackage[justification=centering]{caption}

\setlength{\parindent}{0pt}
\setlength{\textfloatsep}{5pt}
\setlength{\intextsep}{5pt}
\hypersetup{
    colorlinks=true,
    linkcolor=red,
    filecolor=magenta,
    citecolor=blue
    urlcolor=blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}

\newcommand{\acom}[1]{{\color{violet}(#1)}}
\newcommand{\okcom}[1]{{\color{blue}#1}}

\graphicspath{ {./images/} }

\title{Simulation par HPC de dynamique causal de graphe quantique}
\author{ Joseph TOUZET \\
encadré par Pablo ARRIGHI et Oguz KAYA \\
laboratoires LMF et LISN}
\date{Juin 2021}

\begin{document}

\maketitle

\abstract{
La physique quantique permet d'étudier des superpositions d'objets, et de prédire l'évolution de cette superposition. En plus d'étudier une superposition de particules, on peut aussi étudier une superposition de l'espace sur lequel se trouve ces particules. \\

Cet espace sera ici un graphe circulaire, et les dynamique étudiée pourront créer et détruire des noeuds. Ce modèle peut modéliser une dilatation ou contraction de l'espace, qui serait quantifié.

Nous chercherons à avoir une implémentation efficace de ce modèle (parallélisme, calcul distribué, etc...) car la complexité de la simulation quantique est au-moins exponentiel (car le nombre de graphes croit de manière exponentielle), et à concevoir une dynamique causant une croissance exponentielle de la taille moyenne des graphes, qui serait un modèle jouet de l'inflation pour un espace quantifié. 
}

\pagebreak{}

\section{Introduction}

Les graphes que nous étudions dans ce modèle jouet sont des cycles, où des particules peuvent se trouver ou non dans deux position par noeud: le "port gauche" et le "port droit" qui dans l'étape de pas correspondent aux particules qui se déplacent respectivement vers la gauche et vers la droite.

\begin{figure}[ht]
\centering
\begin{minipage}{0.47\textwidth}
\raggedleft
\includegraphics[width=3cm]{introduction}
\end{minipage}
\hspace{\fill} % note: no blank line here
\begin{minipage}{0.47\textwidth}
\caption{Exemple de graphe\\
1: Une particule au port gauche\\
2: Une particule au port droit\\
3: Noeud sans particule\\
4: Une particule sur chaque port}
\end{minipage}
\end{figure}

On peut ensuite appliquer à ces graphes des dynamique qui déterminent le futur état d'un noeud du graphe à partir de son état et de l'état de ses voisins. Une dynamique peut aussi créer ou détruire des noeuds et particules. \\

Il est intéressant de noter qu'une dynamique réversible peut causer une croissance du nombre de noeuds \cite{meyer1}. Nous nous posons donc la question de cette variation du nombre de noeuds si nous appliquons cette dynamique de manière analogue à une marche quantique \cite{meyer2}. Est-il alors possible d'observer une croissance qui ne suit pas la moyenne classique ? \\

Pour répondre à ces questions il est important d'avoir une implémention de ce modèle extrêmement efficace, dont la programmation est le sujet de mon stage.

\section{ Dynamique classique }

Les dynamiques que nous étudierons peuvent être représentées par un ensemble de 2 motifs locaux qui sont échangés par la dynamique.

\begin{figure}[ht]
\begin{minipage}{0.50\textwidth}
\centering
\includegraphics[width=3cm]{split_merge}
\caption{motifs échangés par SM}
\end{minipage}
\begin{minipage}{0.50\textwidth}
\vspace*{0.4cm}
\centering\includegraphics[width=2cm]{coin}
\vspace*{0.2cm}
\caption{motifs échangés par la dynamique coin}
\end{minipage}

\vspace*{0cm} % vertical separation

\begin{minipage}{0.40\textwidth}
\centering
\includegraphics[width=2cm]{erase_create}
\caption{motifs échangés par EC}
\end{minipage}
\begin{minipage}{0.60\textwidth}
\centering
\includegraphics[width=10cm]{move}
\caption{motifs échangé par M}
\end{minipage}

\captionsetup{labelformat=empty}
\caption{motifs échangés par les différentes dynamiques}

\end{figure}

Les différentes dynamiques étudiées jusqu'ici sont:

\begin{itemize}
\itemsep0em
    \item La dynamique "erase create" (notée EC) permet la création de particules, mais ne "merge" ou "split" pas de noeuds.

    \item La dynamique "split merge" (notée SM) permet la création (par "split") et la destruction (par "merge") de noeuds, mais conserve le nombre de particules.

    \item L'étape de pas (notée M et qui sera toujours classique) fais simplement bouger les particules dans le port gauche d'un noeud vers le port gauche du noeud à leur gauche, et inversement pour les particules allant à droite. Cette dynamique peut être très simplement inversé en déplaçant les particules à droite vers la gauche et inversement.

    \item La dynamique coin est une dynamique qui permet une marche quantique en faisant changer de direction une particule.
\end{itemize}

\subsection{ Arithmétique de nom }
\label{ssec:arbre}

Il est nécessaire de nommer les noeuds \cite{noms1} pour conserver la réversibilité \cite{noms2}. Cette condition nous donne aussi :

\begin{itemize}
\itemsep0em
    \item $\left(u \vee v\right).l = u$
    \item $\left(u \vee v\right).r = v$
    \item $u.r \vee u.l = u$
\end{itemize}

En prenant comme noms de départ des entiers naturels, on peut représenter les noms de noeud comme des arbres, par exemple:\\

\hfil
\Tree [ .{$\left( 0.r \vee 1 \right) \vee 2.l$}
[ .{$0.r \vee 1$}
[ .{$0.r$}
0
{$.r$} ]
1 ]
[ .{$2.l$}
2
{$.l$} ] ]

\section{ Dynamique quantique }

\subsection{ Paramétrisation }

Pour que la dynamique soit bien parametrisée, il faut que l'opération soit Hermitienne et unitaire. On trouve assez simplement qu'une tel matrice 2x2 peut être parametrisée par 2 angles réels :

$$
U = \begin{pmatrix}
cos \theta & sin \theta e^{i\phi}\\ 
sin \theta e^{-i\phi} & -cos \theta
\end{pmatrix}
$$

Et en se plaçant dans la base "locale" (les deux motifs échangés par la dynamique) d'une des dynamique, on trouve trivialement les amplitudes caractéristiques de la dynamique :

\begin{itemize}
\itemsep0em
    \item $sin \theta e^{i\phi} $ pour l'application dans le sens direct.
    \item $cos \theta $ pour la non-application dans le sens direct.
    \item $sin \theta e^{-i\phi} $ pour l'application dans le sens contraire.
    \item $cos \theta $ pour la non-application dans le sens contraire.
\end{itemize}

On remarque que l'angle $\phi$ peut favoriser ou non les interférences destructives ou constructives en influençant la phase relative de graphes ayant eu un différent nombre d'opération. \\

L'angle $\theta$ influence quant à lui la probabilité d'application par rapport à la probabilité de non-application. On a donc la dynamique classique pour $\theta = \frac{\pi}{2}$, on a aucun changement d'une itération à l'autre pour $\theta = 0$, et des dynamique intermédiaire pour $\theta$ entre $0$ et $\frac{\pi}{2}$.

\section{ Implémentation }

L'implémentation que j'ai codé lors de ce stage est codé en C++, en reposant sur OpenMP pour le parallélisme et la bibliothèque \href{http://www.mpfr.org}{MPFR} pour permettre une plus grande précision de flottants dont nous avons besoin dans le calcul des probabilités.

\subsection{ Difficultés }

Le nom des noeuds doit être représenté par un arbre binaire (cf section \ref{ssec:arbre}), ce qui est une structure de donnée irrégulière et peut donc facilement limiter la vitesses d'accès mémoire en causant de la fragmentation en fonction des implémentions et de leur flexibilité. \\

On a une croissance exponentielle du nombre de graphes puisque chaque graphe tend à avoir un nombre constant en moyenne de sous-graphes engendrés après une étape de dynamique quantique. Ce qui nous condamne à être limités en mémoire après un faible nombre d'itérations.  \\

De plus chaque graphes est un relativement petit objet, et en créer et en détruire en permanence force un grand nombre d'allocation est désallocation de petit objet ce qui peut être très coûteux. \\

La dynamique quantique crée des graphes identiques qui doivent interférer (leurs amplitudes doivent être sommées) ce qui nous force à opérer un grand nombre de comparaisons d'objets irréguliers.

\subsection{ Techniques utilisé }

Nous représentons les noms de noeuds de manière continue en mémoire en utilisant des vecteurs d'indices à gauche et à droite plutôt que des containers. Ce qui nous force à prévoir le nombre maximal de noeuds dans ces arbres avant de créer les graphes.  \\

De plus, chaque propriété, relatives aux graphes individuels, aux noeuds ou aux arbre de noeud, est représentée sous la forme d'un seul vecteur contiguë (que l'on ne fait qu'agrandir si besoin, sans jamais le rétrécir, et en s'interdisant les insertion et les suppression). On se limite donc à une faible nombre constant (autour d'un vingtaine) de grand objet contiguë, ce qui permet de meilleurs accès mémoire en évitant la fragmentation. \\

Pour limiter la croissance exponentielle, nous gardons les N graphes les plus probables après chaque itération. Nous prenons N le plus grand possible sans pour autant remplir l'entièreté de la mémoire disponible (N est de l'ordre de $10^{7}$ pour une machine avec 128Go de mémoire et pour des graphes de 10 noeud de départ). \\

Pour pouvoir garder une représentation continue en mémoire de tout nos objets, et pour simplifier les interférences on commence par une itération symbolique où:

\begin{itemize}
\itemsep0em
    \item On calcule la taille de chaque objet à la prochaine itération pour pouvoir assigner des espaces mémoire continus (sur les vecteurs décris précédemment) pour chacun d'entre eux ce qui permettra leur accès en parallèle sans risque de ré-allocation.
    \item On calcule un hash de chaque graphe, pour ensuite effectuer l'interférence en les comparant plutôt que de comparer les graphes. On peut ensuite s'assurer de ne générer que des graphes distincts puisque l'interférence se fait à l'itération symbolique plutôt qu'à l'itération finale.
\end{itemize}

Ces techniques nous permettent d'avoir un fort gain de performance avec le nombre de coeurs (gain quasi-linéaire jusqu'à 8 coeur avant d'être limité par la bande passante de la mémoire, et arriver à un gain de 20x pour 32 coeurs).

\section{ Résultats }

\subsection{ Test et validation }

Le test le plus important d'une dynamique quantique est sa réversibilité: on veut s'assurer que après N étapes, on récupère bien l'état de départ avec une probabilité 1 en effectuant N étapes de la dynamique inverse. \\

Sachant que $EC \circ EC = I$ et $SM \circ SM = I$, et en notant $M^{-1}$ tel que $M \circ M^{-1} = I$, on peut trouver simplement l'inverse de règles composé simple:

\begin{itemize}
\itemsep0em
  \item $\left(EC \circ M\right)^{-1} = M^{-1} \circ EC$
  \item $\left(SM \circ M\right)^{-1} = M^{-1} \circ SM$
\end{itemize}

On peut ensuite opérer ce test d'objectivité pour des milliers de graphes aléatoires de tailles différentes, pour des valeurs de N différentes, et pour chacune de ces dynamiques. Permettant ainsi à la fois de vérifier la validité de chaque dynamique mais aussi la validité de l'implémention de l'application d'une dynamique quantique.

\subsection{ Simulation quantiques }

Nous calculons la taille moyenne et le nombre de particules moyen pour un certain nombre d'itérations de chaque règle, et la probabilité totale (pour mesurer l'impact de la suppression de graphes), le nombre de graphes et le ratio du nombre de graphes avant et après interférence. \\

\begin{figure}[h!]
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{sizes/0_erase_create_move}
\caption{$EC\circ M$, $\theta=0.375\pi$}
\end{minipage}
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{sizes/2_erase_create_move}
\caption{$EC\circ M$, $\theta=0.25\pi$}
\end{minipage}
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{sizes/1_erase_create_move}
\caption{$EC\circ M$, $\theta=0.125\pi$}
\end{minipage}

\captionsetup{labelformat=empty}
\caption{Bleu foncé: probabilité total, Rouge: nombre de graphes (échelle log.), bleu clair: ratio du nombre de graphes avant/après interférence }

\end{figure}

On remarque que pour la dynamique $EC \circ M$ (figures 7 à 9, en partant d'un graphe vide) la densité de particules oscille avec une amplitude dépendante de $\theta$ (plus $\theta$ est grand plus la probabilité d'opération est grande, ce qui créer des particules à l'itération N et les détruit à l'itération N-1). \\

\begin{figure}[h!]
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{sizes/0_split_merge_move}
\caption{$SM\circ M$, $\theta=0.375\pi$}
\end{minipage}
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{sizes/1_split_merge_move}
\caption{$SM\circ M$, $\theta=0.25\pi$}
\end{minipage}
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{sizes/2_split_merge_move}
\caption{$SM\circ M$, $\theta=0.125\pi$}
\end{minipage}

\captionsetup{labelformat=empty}
\caption{Bleu: taille moyenne, Rouge: densité moyenne}

\end{figure}

Pour la dynamique $SM \circ M$ (figures 10 à 12) la taille moyenne croît de manière classique (la densité décroît inversement au nombre de noeuds puisque le nombre de particules est constant) pour $\theta \neq 0.25\pi$ mais avec une croissance plus faible pour $\theta$ plus faible. \\

Pour $\theta = 0.125\pi$ On a d'abord une croissance, puis une décroissance lorsque le nombre de graphes explose et que les graphes ayant beaucoup de "split merge" (et donc les plus grand) deviennent exponentiellement moins probables par rapport aux graphes restés de taille constante. Il n'est pas clair si se résultat est uniquement du à la suppression des graphes les moins probables ou non. \\

\begin{figure}[h!]
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{stats/0_split_merge_move}
\caption{$SM\circ M$, $\theta=0.375\pi$}
\end{minipage}
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{stats/1_split_merge_move}
\caption{$SM\circ M$, $\theta=0.25\pi$}
\end{minipage}
\begin{minipage}{0.33\textwidth}
\centering
\includegraphics[width=\textwidth, height=0.66\textwidth]{stats/2_erase_create_move}
\caption{$EC\circ M$, $\theta=0.25\pi$}
\end{minipage}

\captionsetup{labelformat=empty}
\caption{Bleu foncé: probabilité total, Rouge: nombre de graphes (échelle log.), bleu clair: ratio du nombre de graphes avant/après interférence }

\end{figure}

Les instabilités pour la dynamique $SM \circ M$ et $\theta=0.25\pi$ sont expliquées par la figure 15: on peut voir que l'on a une forte perte de probabilité totale, qui est due à une trop faible variation de probabilité des graphe (car $\theta=0.25\pi$) ce qui amène à avoir une perte de probabilité quasi-égale à la proportion de graphe supprimé. \\

On remarque aussi que la croissance du nombre de graphes est très exactement exponentielle (droite en échelle log), et que la dynamique $EC \circ M$ (figure 16) a un comportement typiquement quantique puisque son ratio de graphes est proche de zéro (très grand nombre de graphes qui interagissent) car elle est limité en nombre de graphes par $4^n$ avec n le nombre de noeuds.

\section{ Suite du stage }

Maintenant que l'on a la capacité de faire une simulation quantique, les objectifs pour les 4 prochaine semaine de stage sont:

\begin{itemize}
\itemsep0em
    \item Concevoir une dynamique qui cause une croissance exponentielle du nombre de noeuds.
    \item Observer des comportement typiquement quantique (distinct du comportement probabiliste, et dépendant de l'angle $\phi$).
    \item Observer les limites des approximations faites.
\end{itemize}

\pagebreak{}

\section{ Conclusion }

Les techniques de simulation et programmation, et les approximations utilisées jusqu'ici ont permis d'obtenir des résultat de simulation pour un problème qui, sans approximation est de complexité au moins exponentielle (avec le nombre de graphes). On peut maintenant espérer concevoir une dynamique causant une croissance exponentielle de la taille, bien que certain résultat préliminaires montrent que cette dynamique peut être plus complexe qu'il n'y parait (non-stabilité de la densité avec la règle $EC \circ M$, et une observation récente que une dynamique $EC \circ M \circ SM \circ M$ ou $EC \circ SM \circ M$ a tendance à revenir à l'état de départ et donc à empêcher la croissance). \\

Ce stage est ma première expérience de programmation pour la recherche. C'est aussi la première fois que j'ai eu l'occasion d'utiliser des machines si puissantes, ce qui amène des considération d'HPC que je n'ai jamais eus, et m'a permis de prendre en considération des aspect d'optimisation très enrichissant.

\vfill
\bibliographystyle{abbrv}
\bibliography{biblio}

\end{document}
